### 2015-11-29 paper/paper.tex
initial commit for final report paper

\documentclass[conference]{IEEEtran}
%\usepackage[top=1.2in, bottom=1.5in, left=0.8in, right=0.8in]{geometry}
\usepackage{balance}
\usepackage{graphicx}
\usepackage{xcolor}
\newcommand{\todo}[1]{\qquad\textcolor{red}{TODO: #1}\PackageWarning{TODO:}{#1!}}

\hyphenation{op-tical net-works semi-conduc-tor}

\makeatletter
\setlength{\@fptop}{0pt}
\makeatother

\begin{document}
\title{Togglge Smell Detection in Google Chrome}
\author{
Md Tajmilur Rahman, Dharani Kumar, Sumir Sarkar, Omar Faruk\\
Concordia University,~Montreal,~QC,~Canada
}
\maketitle

\begin{abstract}
TODO
\end{abstract}

\begin{IEEEkeywords}
Software Refactoring, Software Re-Engineering, Software Design, Feature Toggles, Code Smell, Technical Debt, Mining Repository
\end{IEEEkeywords}

\section{Introduction}
TODO

\section{Related Works}
\label{related-works}

\section{Study Setup}
\label{study-setup}

\section{Case Study}
\label{results}
TODO: Answer the research questions

\section{Code Smells}
\label{discussion}
TODO

\section{Results}
\label{threats}
TODO
\subsection{Qualitative}
TODO
\subsection{Quantitative}
TODO

\section{Conclusion}
\label{conclusion}
TODO

\bibliographystyle{abbrv}

\bibliography{paper}

\balance
\end{document}

### 2015-12-03 src/edu/concordia/tsd/smells/deadtoggle/DeadToggleFlagVisitorVisitor.java
Modify the dead_toggle info

@@ -1,0 +1,78 @@
+package edu.concordia.tsd.smells.deadtoggle;
+
+import java.util.HashMap;
+import java.util.HashSet;
+import java.util.Map;
+import java.util.Set;
+
+import org.eclipse.cdt.core.dom.ast.ASTVisitor;
+import org.eclipse.cdt.core.dom.ast.IASTBinaryExpression;
+import org.eclipse.cdt.core.dom.ast.IASTExpression;
+import org.eclipse.cdt.core.dom.ast.IASTFileLocation;
+import org.eclipse.cdt.core.dom.ast.IASTFunctionCallExpression;
+import org.eclipse.cdt.core.dom.ast.IASTInitializerClause;
+import org.eclipse.cdt.core.dom.ast.IASTStatement;
+import org.eclipse.cdt.core.dom.ast.cpp.ICPPASTIfStatement;
+
+/**
+ * @author dharani kumar palani (d_palan@encs.concordia.ca)
+ *
+ */
+public class DeadToggleFlagVisitorVisitor extends ASTVisitor {
+
+	// Map of toggle flag versus locations
+	private Map<String, Set<Integer>> flagLocations = new HashMap<String, Set<Integer>>();
+
+	// The toggle method name used to refine our search.
+	private String toggleMethodName;
+
+	public DeadToggleFlagVisitorVisitor(String toggleMethodName) {
+		super(true);
+		shouldVisitStatements = true;
+		this.toggleMethodName = toggleMethodName;
+	}
+
+	@Override
+	public int visit(IASTStatement statement) {
+		System.out.println("visit(statement)");
+
+		if (statement instanceof ICPPASTIfStatement) {
+			final ICPPASTIfStatement cppIFStatement = (ICPPASTIfStatement) statement;
+
+			IASTExpression conditionalExpr = cppIFStatement.getConditionExpression();
+
+			if (conditionalExpr != null && conditionalExpr instanceof IASTFunctionCallExpression
+					&& conditionalExpr.getRawSignature().contains(toggleMethodName)) {
+				IASTFunctionCallExpression fcexpr = (IASTFunctionCallExpression) conditionalExpr;
+
+				String rawSignature = fcexpr.getRawSignature();
+				System.out.println("rawSignature " + rawSignature);
+
+				IASTFileLocation fileLocation = cppIFStatement.getFileLocation();
+				System.out.println("starting line number " + fileLocation.getStartingLineNumber());
+				
+				IASTInitializerClause[] arguments = fcexpr.getArguments();
+				
[…]

### 2015-12-03 src/edu/concordia/tsd/util/DeadToggle.java
Add two class to get all the deadToggle values from file

@@ -1,0 +1,21 @@
+package edu.concordia.tsd.util;
+
+public class DeadToggle {
+	
+	private String toggleValue;
+	private String toggleFlagName;
+	
+	public String getToggleValue() {
+		return toggleValue;
+	}
+	public void setToggleValue(String toggleValue) {
+		this.toggleValue = toggleValue;
+	}
+	public String getToggleFlagName() {
+		return toggleFlagName;
+	}
+	public void setToggleFlagName(String toggleFlagName) {
+		this.toggleFlagName = toggleFlagName;
+	}
+
+}

### 2015-12-03 src/edu/concordia/tsd/util/DeadToggleReadedFromFile.java

@@ -1,0 +1,77 @@
+package edu.concordia.tsd.util;
+
+import java.io.BufferedReader;
+import java.io.FileNotFoundException;
+import java.io.FileReader;
+import java.io.IOException;
+import java.util.ArrayList;
+import java.util.List;
+import java.util.StringTokenizer;
+
+public class DeadToggleReadedFromFile {
+
+	private final String PATH = "resources/dead_toggles.txt";
+	private BufferedReader reader;
+
+	private String strLine = "";
+	private StringTokenizer st = null;
+	int lineNumber = 0;
+	int tokenNumber = 0;
+
+	public DeadToggleReadedFromFile() throws FileNotFoundException {
+		reader = new BufferedReader(new FileReader(PATH));
+	}
+
+	private List<DeadToggle> getDeadToggles() throws FileNotFoundException, IOException {
+
+		List<DeadToggle> deadToggleList = new ArrayList<DeadToggle>();
+
+		while ((strLine = reader.readLine()) != null) {
+			lineNumber++;
+
+			if (lineNumber != 1 && lineNumber != 2) {
+
+				st = new StringTokenizer(strLine, "|");
+				DeadToggle deadToggleObj = new DeadToggle();
+
+				while (st.hasMoreTokens()) {
+					// display dead toggle values
+					tokenNumber++;
+
+					if (tokenNumber == 1)
+						deadToggleObj.setToggleValue(st.nextToken().replace("--", "").trim());
+					else if (tokenNumber == 2) {
+						deadToggleObj.setToggleFlagName(st.nextToken().trim());
+					} else {
+						st.nextToken();
+					}
+
+					// System.out.println("Line # " + lineNumber + ", Token # "
+					// + tokenNumber + ", Token : " + st.nextToken());
+
+				}
+
+				// reset token number
+				tokenNumber = 0;
+				// Add DeadToggle Object into List
+				deadToggleList.add(deadToggleObj);
+			}
+
+		} // End of While
+		return deadToggleList;
+	}// End of getDeadToggle Method
+
+	public static void main(String[] args) throws IOException {
+		
+		DeadToggleReadedFromFile deadToggleReadedFromFile = new DeadToggleReadedFromFile();
+
+		List<DeadToggle> deadToggleList = deadToggleReadedFromFile.getDeadToggles();
+
+		for (int i = 0; i < deadToggleList.size(); i++) {
[…]

### 2015-12-04 src/edu/concordia/tsd/smells/deadtoggle/DeadToggle.java
Add some util scripting files

@@ -1,4 +1,4 @@
-package edu.concordia.tsd.util;
+package edu.concordia.tsd.smells.deadtoggle;
 
 public class DeadToggle {
 	

### 2015-12-04 src/edu/concordia/tsd/smells/deadtoggle/DeadToggleReadedFromFile.java

@@ -1,4 +1,4 @@
-package edu.concordia.tsd.util;
+package edu.concordia.tsd.smells.deadtoggle;
 
 import java.io.BufferedReader;
 import java.io.FileNotFoundException;

### 2015-12-04 paper/paper.tex
study setip and and the related work

@@
 \author{
-Md Tajmilur Rahman, Dharani Kumar, Sumir Sarkar, Omar Faruk\\
+Md Tajmilur Rahman, Dharani Kumar, Sumir Sarkar, Omar Faruk Miah\\
 Concordia University,~Montreal,~QC,~Canada
@@
 \label{related-works}
+In order to study about the code smells and feature toggle well we have studied many paper but four of them most influential.Separating features in source code: an exploratory study [1] In this paper the researchers investigate about the separation of features in existing code.For the the purpose of the investigation they conducted an exploratory study in the context of two existing systems: \textbf{gnu.regexp and jFTPd}.Their believe about the study feature is that the features of interest to strip out will not always be known a-prior but will emerge as systems evolve.They have proposed two methodologies to separate out the features from the source code which are either tangled within a single method or across several classes.In lightweight separation of concern mechanism is: how far can they get by improving the object-oriented structure that exists in the system to capture features explicitly?
+If the feature is explicit and modularized in an object-oriented structure, then they could use naming conventions (and other simple tools) to help decompose a feature out of a system.The Hyper/J tool allows one to state declaratively what code in an existing set of class files contributes to a particular dimension, and within a dimension to particular concerns.
+AspectJ is an extension to Java to support aspect-oriented programming developed at Xerox PARC.
+They considered two common kinds of feature encodings in two existing Java systems.
+One is tangling of a feature within a method in the gnu.regexp system and another is tangling of a feature between classes in the jFTPd system.These entangling types In first case, probably lost cohesion of Lightweight SOC approach.but the splitting and restructuring was done by manually: moving fields, moving methods, forming methods, modifying inheritance and interface associations.Then they tried to separate these features using their different mechanisms (Hyper/J, AspectJ and lightweight separation of concern mechanism).Tangling in a Single Method is the method they worked with from the gnu.regexp system.
+This method performs part of the regular expression matching functionality.
+It supports several different kinds of matches, including matches across lines, matches where carat characters do not need to match at the beginning of the line and so on.
+Each of these kind of matches corresponds to a different feature.
+They wanted to separate these features that were originally tangled in a single method so as to produce a system that might support, for instance, only multi-line matches.
+Partial Dead Code Elimination [2]The paper presents an algorithm to eliminate partial dead code and to improve the speed of execution of program by moving the unnecessary variable assignment to the farthest location in the control flow graph, without changing the semantics of the program.The algorithm maintains a Graph whose nodes are basic block of statements and edges represents the branching information.
+The partial dead code elimination is a sequence/repetition of assignment sinking and further followed by dead code eliminations.
+The algorithm uses the dead code elimination techniques to eliminate the dead code and repeatedly tries to sink the assignments.
+In that process there are certain second order effects are classified as follows:
+\textbf{Sinking - Elimination Effects}- This is a recursive definition where an assignment statement can be sunk until it can be eliminated by dead code elimination
+\textbf{Sinking - Sinking Effects -} One assignment sinking can lead to sink other assignment statements.
+\textbf{Elimination - Sinking Effects -} Eliminating one or more dead assignments might lead to sinking of other assignment statements.\textbf{Elimination - Elimination Effects -} One dead assignment elimination might lead to subsequent assignment elimination if the control flow graph leading to the end node doesn’t use the variable used in the assignment statement which is being eliminated.
+The algorithm he program addresses all the above second order effects caused by the movement of the assignment statements and also covers arbitrary control flow structures, distinguishes between the profitable code movement across the loop and fatal code movement into the loops.The dead code elimination program runs the following two functions:\textbf{dce}which eliminates the dead assignments by a dead variable analysis data and \textbf{ask} which does assignment sinking in the program by the delayability analysis.Dead variables are identified using a backward directed bit-vector based dataflow analysis technique.
+The dead assignments are identified using definition-use graphs.The delayability analysis is a technique to identify the location in the block of code to hoist a variable assignment.Eliminating dead code from Xquery programs [3]In this paper they propose a technique for performing static basic dead-code analysis and eliminate the dead code from an XQuery program.XQuery is a query and functional programming language basically takes one (or possibly several) XML document as input, performs some computation based on its tree view, and finally outputs a result in the form of another XML document.
+The core of the XQuery language is composed of XPath expressions that make it possible to navigate in the document tree and extract nodes that satisfy some conditions.They use two methodology \textbf{Path-Error Detection} and \textbf{Static Code Refactoring and Highlighting}.In the path-error detection they gave a scema as input to an XQuery program and For each XPath expression occurring in XQuery program, they just check that it is meaningful or not with respect to the constraints described in scema.
+If navigational information contained in a given path contradicts the constraints described in Scema then the path will always return an empty sequence of nodes.All XQuery instructions that depend on that path are dead code and maybe they should remove.For Static Code Refactoring they build an AST that consists in extracting all the path expressions from the program and checking their satisfiability individually.Then, in a second step, these paths are combined with the schema, and checked again for satisfiability.Each kind of unsatisfiable path is marked differently in the AST.each path is considered as a sequence of basic navigation steps possibly with qualifiers.
+The first step is analyzed.
+Then each additional step is successively appended to this initial step and the resulting path is analyzed in turn.
+This makes it possible to identify precisely where the error has been introduced in the path and remove them.An Eclipse Plugin to Support Code Smells using Binary Logistic Regression Model[4]This paper presents an eclipse plugin tool to detect code smells using a technique build upon Binary Logistic Regression Model by using the heuristic of expert knowledge to calibrate the model.BLRM is used for estimating the probability of occurrence of an event by fitting the data set on to a logistic curve.The binary logistic regression with dependent variable having two values (either code smell present or absent) has been used to detect the probability of code smell.The BLR is calibration is done using the statistical tools like R or SPSS and JRI (Java R Inteface) is used to interface with R language from the eclipse plugin.The plugin operates in two different modes (local and remote).The plugin allows the source code to be annotated using a UI action and then collects the metrics from the annotated source code.
+The following metrics are calculated by the plugin for the classes and methods: \textbf{1.
+LOC},\textbf{2.
+Depth of inheritance tree},\textbf{3.
+Number of methods},\textbf{4.
+Lack of cohesion},\textbf{5.
+Number of parameters} and \textbf{5.
+McCabe Cyclomatic Complexity}
 
@@
 \label{study-setup}
-
+In order to explore the feature toggle related smell we have searched for open source projects and found some projects with feature toggle implemented in those project.But we have choose Google Chome as our main code base because it has more then 5 years active development life cycle with feature toggle in it and it is released frequently.So there might be any issue with feature toggle which might not maintain properly.
 \section{Case Study}

### 2015-12-05 paper/paper.tex
resolving conflict

@@
 \author{
-Md Tajmilur Rahman, Dharani Kumar, Sumir Sarkar, Omar Faruk Miah\\
+Md Tajmilur Rahman, Dharani Kumar, Sumit Sarkar, Omar Faruk\\
 Concordia University,~Montreal,~QC,~Canada
@@
 \begin{abstract}
-TODO
+Identifying code smell is the first step to re-factor a software system. 
+In Google Chrome developers use feature toggles to control their features 
+and keep developing on a single trunk. This paper investigates code smell 
+caused by improper use of feature toggles in Google Chrome that we call 
+as toggle smell. Using feature toggles to hide/unhide features is an old 
+concept but recently being practised in many software companies. Improper 
+use of toggles might cause code smell including duplicate code, dead code, 
+coupling and lack of cohesion. We classified the smells caused by toggles 
+in six different patterns Dead Toggles, Tested Toggles, Spaghetti Toggles, 
+Mix of Compile-Time and Runtime Toggles, Legacy toggles and Spread Toggles. 
+We used AST parser tool as an eclipse plug-in to identify these toggle 
+smells in major modules of Google Chrome source code. We found that TODO 
+nested toggles smells, TODO spaghetti toggles and TODO spread toggles in ``chrome'' and ``base'' modules of Google Chrome.
 \end{abstract}

### 2015-12-05 paper/paper.tex
writing case study

@@
 We used AST parser tool as an eclipse plug-in to identify these toggle 
-smells in major modules of Google Chrome source code. We found that TODO 
-nested toggles smells, TODO spaghetti toggles and TODO spread toggles in ``chrome'' and ``base'' modules of Google Chrome.
+smells in major modules of Google Chrome source code. We found TODO 
+nested toggles smells, TODO spaghetti toggles and TODO spread toggles in ``chrome'' and ``base'' modules of Google Chrome.\\
 \end{abstract}
@@
 \label{study-setup}
-In order to explore the feature toggle related smell we have searched for open source projects and found some projects with feature toggle implemented in those project.But we have choose Google Chome as our main code base because it has more then 5 years active development life cycle with feature toggle in it and it is released frequently.So there might be any issue with feature toggle which might not maintain properly.
+For this study we downloaded Google Chrome open source project from the git repository. It has more then 5 years of active development life cycle 
+managing their features using feature toggles.
+
 \section{Case Study}
+We classified toggle smells in different classes based on their usage in 
+the source code. Before that we studied different types of feature toggles 
+available in Google Chrome.
+
+\subsection{Compile Time toggles}
+The first set of usage patterns we descriptively belongs to the compile 
+time toggles. Here changing the toggle value requires modifying the source 
+code and generating a new binary to enable or disable a particular feature 
+for testing or release. The usage also relies upon the support in the 
+programming language for managing enumerations.
+
+Even though the patterns are not complex, they are subtle for small projects (like capstone or startups) in order to manage feature dependencies and 
+avoid feature branching. Another benefit of compile time toggles is, when 
+cleaning up the toggle code at the end of toggle life. The location of the 
+changes could be easily identified by commenting out the field containing the toggle flag.
+
+\subsection{Constants Variables}
+In this pattern the value of the toggle state of a feature is managed through a constant variable declared in the program.
+In languages like C/C++, const modifiers will be used to inform that state of the feature flags will not change throughout the lifetime of the program.
+In Java final modifiers will be used.
+The data type of the variable could be a boolean or integer.\\
+
+For example,  in Java, the constants could be declared in a final static class and used in all source files using static imports.\\
+
+public final class ToggleStates {
+    public static final boolean IS_FEATURE1_ENABLED = true;
+    public static final boolean IS_FEATURE2_ENABLED = true;
+    ... ...
+}
+
+\subsection{Enumerations Interface}
+In Java there is a support to manage set of states through “enum” interface which is much richer when compared to languages like C, C++ (C++11 has similar support).
+The enum can implement interfaces and provide some flexibility in defining the toggle API (Togglz framework uses this approach) to use rather than using the constant variables directly.\\
+
+public enum ToggleFlags
+{
+    FEATURE1(false),
+    FEATURE2(true),
+    FEATURE3(false);\\
+
+    private boolean state;
+    private ToggleFlags(boolean state) { this.state = state; }\\
+
+    public boolean isEnabled() { return this.state; }
+}\\
+
+The client code can directly use this \textit{enum} class method as below ``ToggleFlags.FEATURE1.isEnabled()'' which looks much cleaner in code when compared to accessing the values through constant variables.
+
+\subsection{Compile-Time Macros}
+
 \label{results}
-TODO: Answer the research questions
+TODO:
 
@@
 TODO
+
 \subsection{Qualitative}

### 2015-12-06 src/edu/concordia/tsd/smells/deadtoggle/DeadToggleSmellDetector.java
Fixed the order of checking of the dead toggles.

@@ -86,12 +86,15 @@ public class DeadToggleSmellDetector extends AbstractSmellDetector {
 			IASTInitializerClause[] arguments = fcexpr.getArguments();
 			String argName = arguments[0].getRawSignature();
 
-			if (deadToggles.contains(argName)) {
-				Set<ToggleContext> set = new HashSet<ToggleContext>();
-				ToggleContext tc = new ToggleContext(argName);
-				tc.addFileAndLocation(fcexpr.getContainingFilename(), fcexpr.getFileLocation().getStartingLineNumber());
-				set.add(tc);
-				toggleSmells.add(new ToggleSmell(ToggleSmellType.DEAD_TOGGLE, set));
+			for (String string : deadToggles) {
+				if (string.contains(argName)) {
+					Set<ToggleContext> set = new HashSet<ToggleContext>();
+					ToggleContext tc = new ToggleContext(argName);
+					tc.addFileAndLocation(fcexpr.getContainingFilename(),
+							fcexpr.getFileLocation().getStartingLineNumber());
+					set.add(tc);
+					toggleSmells.add(new ToggleSmell(ToggleSmellType.DEAD_TOGGLE, set));
+				}
 			}
 		}
 	}

### 2015-12-06 src/tsd/handlers/TSDHandler.java
captured the time taken to run a smell detection.

@@ -79,12 +79,16 @@ public class TSDHandler extends AbstractHandler {
 
 					for (IToggleSmellDetector smellDetector : sds) {
 
+						long startTime = System.currentTimeMillis();
+
 						Set<ToggleSmell> allDetectedSmells = smellDetector.getToggleSmells(icProject,
 								TOGGLE_METHOD_NAME, deadToggleFlags);
 						System.out.println("Smell Detector type " + smellDetector.getDetectorType());
 						for (ToggleSmell toggleSmell : allDetectedSmells) {
 							System.out.println(toggleSmell);
 						}
+
+						System.out.println("Time taken " + (System.currentTimeMillis() - startTime) + "ms");
 
 					}
 				}

### 2015-12-06 src/edu/concordia/tsd/smells/detector/AbstractSmellDetector.java
Added an API to count the number of files scanned.

@@ -1,13 +1,10 @@
-/**
- * 
- */
 package edu.concordia.tsd.smells.detector;
 
 import java.util.HashSet;
-import java.util.List;
 import java.util.Set;
 
 import org.eclipse.cdt.core.model.CModelException;
+import org.eclipse.cdt.core.model.ICElement;
 import org.eclipse.cdt.core.model.ICProject;
 import org.eclipse.cdt.core.model.ISourceRoot;
 import org.eclipse.cdt.core.model.ITranslationUnit;
@@ -20,26 +17,15 @@ import edu.concordia.tsd.smells.ToggleSmell;
  */
 public abstract class AbstractSmellDetector implements IToggleSmellDetector {
 
-	/**
-	 * @uml.property name="toggleSmells"
-	 * @uml.associationEnd multiplicity="(0 -1)"
-	 *                     elementType="edu.concordia.tsd.smells.ToggleSmell"
-	 */
 	protected Set<ToggleSmell> toggleSmells = new HashSet<ToggleSmell>();
-	/**
-	 * @uml.property name="icProject"
-	 * @uml.associationEnd
-	 */
+
 	protected ICProject icProject;
-	/**
-	 * @uml.property name="toggleMethodName"
-	 */
+
 	protected String toggleMethodName;
 
-	/**
-	 * @uml.property name="deadToggles"
-	 */
 	protected Set<String> deadToggles;
+
+	private int numFiles = 0;
 
 	public Set<ToggleSmell> getToggleSmells(ICProject icProject, final String methodName, Set<String> deadToggleFlags) {
 		this.icProject = icProject;
@@ -52,12 +38,21 @@ public abstract class AbstractSmellDetector implements IToggleSmellDetector {
 	protected void detectSmells() {
 		ISourceRoot[] allSourceRoots = null;
 		try {
+
 			allSourceRoots = icProject.getAllSourceRoots();
+
+			ICElement[] childrens = icProject.getChildren();
+
+			for (ICElement icElement : childrens) {
+				System.out.println("icElement " + icElement.getElementName());
+			}
+
 			for (ISourceRoot iSourceRoot : allSourceRoots) {
 				ITranslationUnit[] allTU = iSourceRoot.getTranslationUnits();
 
 				for (ITranslationUnit iTranslationUnit : allTU) {
 					if (iTranslationUnit.isCXXLanguage() && iTranslationUnit.isSourceUnit()) {
+						numFiles++;
[…]

### 2015-12-06 src/edu/concordia/tsd/smells/detector/IToggleSmellDetector.java

@@ -13,15 +13,23 @@ import edu.concordia.tsd.smells.ToggleSmellType;
 public interface IToggleSmellDetector {
 
 	/**
-	 * @uml.property name="detectorType"
-	 * @uml.associationEnd
+	 * Returns the smell detector type.
 	 */
 	public ToggleSmellType getDetectorType();
 
 	/**
+	 * @param project
+	 *            - the C++ project to scan
+	 * @param methodName
+	 *            - the toggle method name
 	 * @param deadToggleFlags
-	 *            TODO
+	 * 
 	 * @return the Set of detected toggle smells
 	 */
 	public Set<ToggleSmell> getToggleSmells(ICProject project, String methodName, Set<String> deadToggleFlags);
+
+	/**
+	 * Returns the number of files scanned by this detector.
+	 */
+	public long getNumFilesScanned();
 }

### 2015-12-06 src/edu/concordia/tsd/smells/deadtoggle/DeadToggleSmellDetector.java
Removed the dead toggles parameter from the API and made the dead toggles to be loaded from an external resource.

@@ -26,6 +26,17 @@ import edu.concordia.tsd.smells.detector.AbstractSmellDetector;
  */
 public class DeadToggleSmellDetector extends AbstractSmellDetector {
 
+	private Set<String> deadToggles = null;
+
+	public DeadToggleSmellDetector() {
+		try {
+			deadToggles = new DeadAndStableToggleFlagsLoader().getDeadToggleFlags();
+			System.out.println("deadToggles " + deadToggles);
+		} catch (Exception e) {
+			e.printStackTrace();
+		}
+	}
+
 	@Override
 	public ToggleSmellType getDetectorType() {
 		return ToggleSmellType.DEAD_TOGGLE;
@@ -33,6 +44,12 @@ public class DeadToggleSmellDetector extends AbstractSmellDetector {
 
 	@Override
 	protected void scanTranslationUnit(ITranslationUnit tu) {
+
+		// do not scan and get AST if there are no dead toggles.
+		if (deadToggles == null || deadToggles.isEmpty()) {
+			return;
+		}
+
 		try {
 			IASTTranslationUnit astTU = tu.getAST();
 			astTU.accept(new ToggleMethodNameVisitor());

### 2015-12-06 src/edu/concordia/tsd/smells/detector/AbstractSmellDetector.java

@@ -27,10 +27,9 @@ public abstract class AbstractSmellDetector implements IToggleSmellDetector {
 
 	private int numFiles = 0;
 
-	public Set<ToggleSmell> getToggleSmells(ICProject icProject, final String methodName, Set<String> deadToggleFlags) {
+	public Set<ToggleSmell> getToggleSmells(ICProject icProject, final String methodName) {
 		this.icProject = icProject;
 		this.toggleMethodName = methodName;
-		this.deadToggles = deadToggleFlags;
 		detectSmells();
 		return toggleSmells;
 	}

### 2015-12-06 src/edu/concordia/tsd/smells/detector/IToggleSmellDetector.java

@@ -22,11 +22,9 @@ public interface IToggleSmellDetector {
 	 *            - the C++ project to scan
 	 * @param methodName
 	 *            - the toggle method name
-	 * @param deadToggleFlags
-	 * 
 	 * @return the Set of detected toggle smells
 	 */
-	public Set<ToggleSmell> getToggleSmells(ICProject project, String methodName, Set<String> deadToggleFlags);
+	public Set<ToggleSmell> getToggleSmells(ICProject project, String methodName);
 
 	/**
 	 * Returns the number of files scanned by this detector.

### 2015-12-06 src/tsd/handlers/TSDHandler.java
Removed the unused methods.

@@ -1,19 +1,13 @@
 package tsd.handlers;
 
-import java.util.HashSet;
 import java.util.Set;
 
-import org.eclipse.cdt.core.dom.ast.IASTFileLocation;
-import org.eclipse.cdt.core.dom.ast.IBinding;
-import org.eclipse.cdt.core.index.IIndex;
-import org.eclipse.cdt.core.index.IIndexName;
 import org.eclipse.cdt.core.model.CModelException;
 import org.eclipse.cdt.core.model.CoreModel;
 import org.eclipse.cdt.core.model.ICProject;
 import org.eclipse.core.commands.AbstractHandler;
 import org.eclipse.core.commands.ExecutionEvent;
 import org.eclipse.core.commands.ExecutionException;
-import org.eclipse.core.runtime.CoreException;
 import org.eclipse.jface.viewers.ISelection;
 import org.eclipse.jface.viewers.IStructuredSelection;
 import org.eclipse.ui.handlers.HandlerUtil;
@@ -25,7 +19,7 @@ import edu.concordia.tsd.smells.nestedtoggle.NestedToggleSmellDetector;
 import edu.concordia.tsd.smells.spreadtoggle.ToggleSpreadSmellDetector;
 
 /**
- * Our sample handler extends AbstractHandler, an IHandler base class.
+ * Toggle Smell Detector handler extends AbstractHandler, an IHandler base class.
  * 
  * @see org.eclipse.core.commands.IHandler
  * @see org.eclipse.core.commands.AbstractHandler
@@ -66,11 +60,9 @@ public class TSDHandler extends AbstractHandler {
 		ICProject[] allProjects;
 		try {
 
-			Set<String> deadToggleFlags = loadDeadToggleFlags();
-
 			allProjects = CoreModel.getDefault().getCModel().getCProjects();
-			IToggleSmellDetector[] sds = new IToggleSmellDetector[] { new NestedToggleSmellDetector(),
-					new ToggleSpreadSmellDetector(), new DeadToggleSmellDetector() };
+			IToggleSmellDetector[] sds = new IToggleSmellDetector[] { new ToggleSpreadSmellDetector(),
+					new NestedToggleSmellDetector(), new DeadToggleSmellDetector() };
 
 			for (ICProject icProject : allProjects) {
 				System.out.println("icProject " + icProject.getElementName());
@@ -82,7 +74,7 @@ public class TSDHandler extends AbstractHandler {
 						long startTime = System.currentTimeMillis();
 
[…]

### 2015-12-06 src/edu/concordia/tsd/smells/deadtoggle/DeadAndStableToggleFlagsLoader.java
Added another method to check the presence of toggle flag name and value and put them into the list.

@@ -1,0 +1,110 @@
+package edu.concordia.tsd.smells.deadtoggle;
+
+import java.io.BufferedReader;
+import java.io.FileNotFoundException;
+import java.io.FileReader;
+import java.io.IOException;
+import java.util.ArrayList;
+import java.util.HashSet;
+import java.util.List;
+import java.util.Set;
+import java.util.StringTokenizer;
+
+/**
+ * @author Sumit Sarkar
+ */
+public class DeadAndStableToggleFlagsLoader {
+
+	private final String DEAD_TOGGLE_REPO = "resources/dead_toggles.txt";
+	private BufferedReader reader;
+
+	private String strLine = "";
+	private StringTokenizer st = null;
+	int lineNumber = 0;
+	int tokenNumber = 0;
+
+	public DeadAndStableToggleFlagsLoader() throws FileNotFoundException {
+		reader = new BufferedReader(new FileReader(DEAD_TOGGLE_REPO));
+	}
+
+	public Set<String> getDeadToggleFlags() {
+		Set<String> deadToggleFlags = null;
+
+		try {
+			List<DeadToggle> deadToggleList = getDeadToggles();
+
+			if (deadToggleList != null && !deadToggleList.isEmpty()) {
+
+				deadToggleFlags = new HashSet<String>();
+
+				for (DeadToggle deadToggle : deadToggleList) {
+					if (deadToggle.getToggleFlagName().isEmpty()) {
+						deadToggleFlags.add(deadToggle.getToggleValue());
+					} else {
+						deadToggleFlags.add(deadToggle.getToggleFlagName());
+					}
+				}
+			}
+
+		} catch (Exception e) {
+		}
+
+		return deadToggleFlags;
+	}
+
+	private List<DeadToggle> getDeadToggles() throws FileNotFoundException, IOException {
+
+		List<DeadToggle> deadToggleList = new ArrayList<DeadToggle>();
+
+		while ((strLine = reader.readLine()) != null) {
+			lineNumber++;
+
+			if (lineNumber != 1 && lineNumber != 2) {
+
+				st = new StringTokenizer(strLine, "|");
+				DeadToggle deadToggleObj = new DeadToggle();
+
+				while (st.hasMoreTokens()) {
+					// display dead toggle values
+					tokenNumber++;
+
+					if (tokenNumber == 1)
+						deadToggleObj.setToggleValue(st.nextToken().replace("--", "").trim());
+					else if (tokenNumber == 2) {
[…]

### 2015-12-06 src/edu/concordia/tsd/smells/combtoggle/CombIFstatementsVisitor.java
Combinatorial toggle smell detection implementations.

@@ -1,0 +1,135 @@
+package edu.concordia.tsd.smells.combtoggle;
+
+import java.util.HashSet;
+import java.util.Set;
+
+import org.eclipse.cdt.core.dom.ast.ASTVisitor;
+import org.eclipse.cdt.core.dom.ast.IASTExpression;
+import org.eclipse.cdt.core.dom.ast.IASTInitializerClause;
+import org.eclipse.cdt.core.dom.ast.IASTNode;
+import org.eclipse.cdt.core.dom.ast.IASTStatement;
+import org.eclipse.cdt.core.dom.ast.cpp.ICPPASTBinaryExpression;
+import org.eclipse.cdt.core.dom.ast.cpp.ICPPASTFunctionCallExpression;
+import org.eclipse.cdt.core.dom.ast.cpp.ICPPASTIfStatement;
+import org.eclipse.cdt.core.dom.ast.cpp.ICPPASTUnaryExpression;
+import org.eclipse.cdt.core.model.ITranslationUnit;
+
+import edu.concordia.tsd.smells.ToggleContext;
+import edu.concordia.tsd.smells.ToggleSmell;
+import edu.concordia.tsd.smells.ToggleSmellType;
+
+/**
+ * An AST visitor which checks only for the
+ * 
+ * @author dharani kumar palani (d_palan@encs.concordia.ca)
+ *
+ */
+public class CombIFstatementsVisitor extends ASTVisitor {
+
+	private ITranslationUnit tu;
+	private String toggleMethodName;
+
+	private Set<ToggleSmell> toggleSmells = new HashSet<ToggleSmell>();
+
+	public CombIFstatementsVisitor(final ITranslationUnit tu, final String toggleMethodName) {
+		super(true);
+		this.tu = tu;
+		this.toggleMethodName = toggleMethodName;
+		shouldVisitStatements = true;
+	}
+
+	@Override
+	public int visit(IASTStatement statement) {
+
+		IASTNode originalNode = statement.getOriginalNode();
+
+		if (!originalNode.getFileLocation().getFileName().contains(tu.getElementName())) {
+			return PROCESS_CONTINUE;
+		}
+
+		if (statement instanceof ICPPASTIfStatement) {
+			final ICPPASTIfStatement cppIFStatement = (ICPPASTIfStatement) statement;
+			IASTExpression conditionalExpression = cppIFStatement.getConditionExpression();
+
+			if (conditionalExpression != null && conditionalExpression instanceof ICPPASTBinaryExpression) {
[…]

### 2015-12-06 src/edu/concordia/tsd/smells/combtoggle/CombinatorialToggleSmellDetector.java

@@ -1,0 +1,57 @@
+package edu.concordia.tsd.smells.combtoggle;
+
+import java.util.Set;
+
+import org.eclipse.cdt.core.dom.ast.IASTTranslationUnit;
+import org.eclipse.cdt.core.model.ITranslationUnit;
+import org.eclipse.core.runtime.CoreException;
+
+import edu.concordia.tsd.smells.ToggleSmell;
+import edu.concordia.tsd.smells.ToggleSmellType;
+import edu.concordia.tsd.smells.detector.AbstractSmellDetector;
+
+/**
+ * This toggle smell detector will detect smells of using combinatorial toggles
+ * for an execution of a code block. This is a file level toggle smell.
+ * 
+ * @author dharani kumar palani (d_palan@encs.concordia.ca)
+ *
+ */
+public class CombinatorialToggleSmellDetector extends AbstractSmellDetector {
+
+	/*
+	 * (non-Javadoc)
+	 * 
+	 * @see
+	 * edu.concordia.tsd.smells.detector.IToggleSmellDetector#getDetectorType()
+	 */
+	@Override
+	public ToggleSmellType getDetectorType() {
+		return ToggleSmellType.COMBINATORIAL_TOGGLE;
+	}
+
+	/*
+	 * (non-Javadoc)
+	 * 
+	 * @see edu.concordia.tsd.smells.detector.AbstractSmellDetector#
+	 * scanTranslationUnit(org.eclipse.cdt.core.model.ITranslationUnit)
+	 */
+	@Override
+	protected void scanTranslationUnit(ITranslationUnit tu) {
+
+		IASTTranslationUnit iastTU;
+		try {
+			iastTU = tu.getAST();
+			CombIFstatementsVisitor visitor = new CombIFstatementsVisitor(tu, toggleMethodName);
+			iastTU.accept(visitor);
+
+			Set<ToggleSmell> smells = visitor.getSmells();
+
+			if (!smells.isEmpty()) {
+				this.toggleSmells.addAll(smells);
+			}
+		} catch (CoreException e) {
+			e.printStackTrace();
+		}
+	}
+}

### 2015-12-06 paper/paper.tex
Added algorithms, limitations

--- 2015-12-04 paper/paper.tex
@@
 \usepackage{xcolor}
+\usepackage{enumitem}
+\setlength{\parindent}{4em}
+\newcommand{\forceindent}{\leavevmode{\parindent=4em\indent}}
 \newcommand{\todo}[1]{\qquad\textcolor{red}{TODO: #1}\PackageWarning{TODO:}{#1!}}
@@
 \hyphenation{op-tical net-works semi-conduc-tor}
+
+\newenvironment{steps}[1]{\begin{enumerate}[label=#1 \arabic*]}{\end{enumerate}}
+\makeatletter% http://tex.stackexchange.com/questions/29517/forcing-new-line-after-item-number-in-enumerate-environment/29518#29518
+\def\step{%
+   \@ifnextchar[ \@step{\@noitemargtrue\@step[\@itemlabel]}}
+\def\@step[#1]{\item[#1]\mbox{}\\\hspace*{\dimexpr-\labelwidth-\labelsep}}
+\makeatother
+
+\usepackage{listings}
+\usepackage{color}
+
+\definecolor{dkgreen}{rgb}{0,0.6,0}
+\definecolor{gray}{rgb}{0.5,0.5,0.5}
+\definecolor{mauve}{rgb}{0.58,0,0.82}
+
+\lstset{frame=tb,
+  language=Java,
+  aboveskip=3mm,
+  belowskip=3mm,
+  showstringspaces=false,
+  columns=flexible,
+  basicstyle={\small\ttfamily},
+  numbers=none,
+  numberstyle=\tiny\color{gray},
+  keywordstyle=\color{blue},
+  commentstyle=\color{dkgreen},
+  stringstyle=\color{mauve},
+  breaklines=true,
+  breakatwhitespace=true,
+  tabsize=3
+}
 
@@
 \section{Introduction}
-TODO
 
@@
 \label{related-works}
-In order to study about the code smells and feature toggle well we have studied many paper but four of them most influential.Separating features in source code: an exploratory study [1] In this paper the researchers investigate about the separation of features in existing code.For the the purpose of the investigation they conducted an exploratory study in the context of two existing systems: \textbf{gnu.regexp and jFTPd}.Their believe about the study feature is that the features of interest to strip out will not always be known a-prior but will emerge as systems evolve.They have proposed two methodologies to separate out the features from the source code which are either tangled within a single method or across several classes.In lightweight separation of concern mechanism is: how far can they get by improving the object-oriented structure that exists in the system to capture features explicitly?
-If the feature is explicit and modularized in an object-oriented structure, then they could use naming conventions (and other simple tools) to help decompose a feature out of a system.The Hyper/J tool allows one to state declaratively what code in an existing set of class files contributes to a particular dimension, and within a dimension to particular concerns.
-AspectJ is an extension to Java to support aspect-oriented programming developed at Xerox PARC.
-They considered two common kinds of feature encodings in two existing Java systems.
-One is tangling of a feature within a method in the gnu.regexp system and another is tangling of a feature between classes in the jFTPd system.These entangling types In first case, probably lost cohesion of Lightweight SOC approach.but the splitting and restructuring was done by manually: moving fields, moving methods, forming methods, modifying inheritance and interface associations.Then they tried to separate these features using their different mechanisms (Hyper/J, AspectJ and lightweight separation of concern mechanism).Tangling in a Single Method is the method they worked with from the gnu.regexp system.
-This method performs part of the regular expression matching functionality.
-It supports several different kinds of matches, including matches across lines, matches where carat characters do not need to match at the beginning of the line and so on.
-Each of these kind of matches corresponds to a different feature.
-They wanted to separate these features that were originally tangled in a single method so as to produce a system that might support, for instance, only multi-line matches.
-Partial Dead Code Elimination [2]The paper presents an algorithm to eliminate partial dead code and to improve the speed of execution of program by moving the unnecessary variable assignment to the farthest location in the control flow graph, without changing the semantics of the program.The algorithm maintains a Graph whose nodes are basic block of statements and edges represents the branching information.
-The partial dead code elimination is a sequence/repetition of assignment sinking and further followed by dead code eliminations.
+Now a days continuous delivery of a software product is common in software industry.
+In order to maintain the existing features and adding or removing new features in a software system is becoming the harder thing in terms of maintains.
+To keep track and handle the features in some software system toggling is used.In order to study about the code smells and feature toggle, we have studied many paper but four of them most influential.\\
+\forceindent Jens Knoop, Oliver Ruthing, Bernhard Steffen have worked on Partial Dead Code Elimination.
+They present an algorithm to eliminate partial dead code and to improve the speed of execution of program by moving the unnecessary variable assignment (Faint assignment) to the farthest location in the control flow graph, without changing the semantics of the program.
+The algorithm maintains a Graph whose nodes are basic block of statements and edges represents the branching information.
 The algorithm uses the dead code elimination techniques to eliminate the dead code and repeatedly tries to sink the assignments.
 In that process there are certain second order effects are classified as follows:
-\textbf{Sinking - Elimination Effects}- This is a recursive definition where an assignment statement can be sunk until it can be eliminated by dead code elimination
-\textbf{Sinking - Sinking Effects -} One assignment sinking can lead to sink other assignment statements.
-\textbf{Elimination - Sinking Effects -} Eliminating one or more dead assignments might lead to sinking of other assignment statements.\textbf{Elimination - Elimination Effects -} One dead assignment elimination might lead to subsequent assignment elimination if the control flow graph leading to the end node doesn’t use the variable used in the assignment statement which is being eliminated.
-The algorithm he program addresses all the above second order effects caused by the movement of the assignment statements and also covers arbitrary control flow structures, distinguishes between the profitable code movement across the loop and fatal code movement into the loops.The dead code elimination program runs the following two functions:\textbf{dce}which eliminates the dead assignments by a dead variable analysis data and \textbf{ask} which does assignment sinking in the program by the delayability analysis.Dead variables are identified using a backward directed bit-vector based dataflow analysis technique.
-The dead assignments are identified using definition-use graphs.The delayability analysis is a technique to identify the location in the block of code to hoist a variable assignment.Eliminating dead code from Xquery programs [3]In this paper they propose a technique for performing static basic dead-code analysis and eliminate the dead code from an XQuery program.XQuery is a query and functional programming language basically takes one (or possibly several) XML document as input, performs some computation based on its tree view, and finally outputs a result in the form of another XML document.
-The core of the XQuery language is composed of XPath expressions that make it possible to navigate in the document tree and extract nodes that satisfy some conditions.They use two methodology \textbf{Path-Error Detection} and \textbf{Static Code Refactoring and Highlighting}.In the path-error detection they gave a scema as input to an XQuery program and For each XPath expression occurring in XQuery program, they just check that it is meaningful or not with respect to the constraints described in scema.
-If navigational information contained in a given path contradicts the constraints described in Scema then the path will always return an empty sequence of nodes.All XQuery instructions that depend on that path are dead code and maybe they should remove.For Static Code Refactoring they build an AST that consists in extracting all the path expressions from the program and checking their satisfiability individually.Then, in a second step, these paths are combined with the schema, and checked again for satisfiability.Each kind of unsatisfiable path is marked differently in the AST.each path is considered as a sequence of basic navigation steps possibly with qualifiers.
-The first step is analyzed.
-Then each additional step is successively appended to this initial step and the resulting path is analyzed in turn.
-This makes it possible to identify precisely where the error has been introduced in the path and remove them.An Eclipse Plugin to Support Code Smells using Binary Logistic Regression Model[4]This paper presents an eclipse plugin tool to detect code smells using a technique build upon Binary Logistic Regression Model by using the heuristic of expert knowledge to calibrate the model.BLRM is used for estimating the probability of occurrence of an event by fitting the data set on to a logistic curve.The binary logistic regression with dependent variable having two values (either code smell present or absent) has been used to detect the probability of code smell.The BLR is calibration is done using the statistical tools like R or SPSS and JRI (Java R Inteface) is used to interface with R language from the eclipse plugin.The plugin operates in two different modes (local and remote).The plugin allows the source code to be annotated using a UI action and then collects the metrics from the annotated source code.
+\textbf{Sinking - Elimination Effects},
+\textbf{Sinking - Sinking Effects},
+\textbf{Elimination - Sinking Effects} and \textbf{Elimination - Elimination Effects}.
+The algorithm addresses all the above second order effects caused by the movement of the assignment statements and also covers arbitrary control flow structures, distinguishes between the profitable code movement across the loop and fatal code movement into the loops.
+The dead code elimination program runs the following two functions:\textbf{dce} which eliminates the dead assignments by a dead variable analysis data and \textbf{ask} which does assignment sinking in the program by the delayability analysis.Dead variables are identified using a backward directed bit-vector based dataflow analysis technique.
+The dead assignments are identified using definition-use graphs.The delayability analysis is a technique to identify the location in the block of code to hoist a variable assignment.\\
+\forceindent Like their study we can identify the various taxonomies of toggle flag like \textbf{“INVALID TOGGLE”} and \textbf{“STABLE TOGGLE”} usages and smells  in a code base.
+We could leverage their techniques to see the impact of the toggle flag in the further parts of the program either in same program artifact or other artifacts so as to identify the way for their elimination.
+We would like to know the impacts of removing certain variable assignments (in our case toggle flags) and how it will impact the control flow structures.\\\\
+\forceindent Tiago Pessoa and his colleagues develop an Eclipse Plugin to support Code Smells using Binary Logistic Regression Model.
+Their tool is for detecting code smells using BLRM by using the heuristic of expert knowledge to calibrate the model.
+BLRM is used for estimating the probability of occurrence of an event by fitting the data set on to a logistic curve.
+The binary logistic regression with dependent variable having two values (either code smell present or absent) has been used to detect the probability of code smell.
+The BLR is calibration is done using the statistical tools like R or SPSS and JRI (Java R Inteface) is used to interface with R language from the eclipse plugin.
+The plugin operates in two different modes (local and remote).
+The plugin allows the source code to be annotated using a UI action and then collects the metrics from the annotated source code.
 The following metrics are calculated by the plugin for the classes and methods: \textbf{1.
@@
 Number of parameters} and \textbf{5.
-McCabe Cyclomatic Complexity}
+McCabe Cyclomatic Complexity}\\
+\forceindent The authors have used binary logistic regression model in their plugin development to determine the outcome of a code smell.
+We could leverage this technique to create a statistical model to determine whether there is a toggle related code smell by collecting data from the source code and using heuristic knowledge about the toggle.
+For example to determine whether a code block covered by a  “STABLE TOGGLE” is a potential candidate for refactoring the BLR can be trained with the meta data such as time the toggle was introduced, number of state changes during development, number of state changes in the field, number of bugs etc and the BLR can come with the prediction to indicate potential refactorings.\\\\
+\forceindent Gail C.
+Murphy and his colleagues investigate about the separation of features in existing code.For the the purpose of the investigation they conducted an exploratory study in the context of two existing systems: \textbf{gnu.regexp and jFTPd}.
+They have proposed two methodologies to separate out the features from the source code which are either tangled within a single method or across several classes.
+In lightweight separation of concern mechanism: they discussed how far can they get by improving the object-oriented structure that exists in the system to capture features explicitly?
+If the feature is explicit and modularized in an object-oriented structure, then how they could use naming conventions (and other simple tools) to help decompose a feature out of a system.
+How the tool like Hyper/J tool could help to identify the code in an existing set of class files contributes to a particular dimension, and within a dimension to particular concerns.\\
+They considered two common kinds of feature encodings in two existing Java systems.
+One is tangling of a feature within a method in the gnu.regexp system and another is tangling of a feature between classes in the jFTPd system.These entangling types In first case, probably lost cohesion of Lightweight SOC approach.
+But the splitting and restructuring was done by manually: moving fields, moving methods, forming methods, modifying inheritance and interface associations.
+Then they tried to separate these features using their different mechanisms (Hyper/J, AspectJ and lightweight separation of concern mechanism).
+Tangling in a Single Method is the method they worked with from the gnu.regexp system.
+This method performs part of the regular expression matching functionality.
+It supports several different kinds of matches, including matches across lines, matches where carat characters do not need to match at the beginning of the line and so on.
+Each of these kind of matches corresponds to a different feature.
+They wanted to separate these features that were originally tangled in a single method so as to produce a system that might support, for instance, only multi-line matches.\\
+\forceindent In our research objective we have to classify the code smells related to the usage of features toggles.
+One such code smell is to identify the distribution of the same toggles flag among various sources files, we have named this as “TOGGLE SPREAD”.
+This indicates the loose cohesion of a feature.
+This study is used to identify the features from the source code using Aspect oriented programming.\\
+\newline \forceindent Pierre Genevès and Nabil Layaïda analysis, how to detect and remove dead code from Xquery programs.
+They propose a technique for performing static basic dead-code analysis and eliminate the dead code from an XQuery program.
+XQuery is a query and functional programming language basically takes one (or possibly several) XML document as input, performs some computation based on its tree view, and finally outputs a result in the form of another XML document.
+The core of the XQuery language is composed of XPath expressions that make it possible to navigate in the document tree and extract nodes that satisfy some conditions.
+They use two methodology \textbf{Path-Error Detection} and \textbf{Static Code Refactoring and Highlighting}.
+In the path-error detection they gave a scema as input to an XQuery program and For each XPath expression occurring in XQuery program, they just check that it is meaningful or not with respect to the constraints described in scema.
+If navigational information contained in a given path contradicts the constraints described in Scema then the path will always return an empty sequence of nodes.
+All XQuery instructions that depend on that path are dead code and maybe they should remove.
+For Static Code Refactoring they build an AST that consists in extracting all the path expressions from the program and checking their satisfiability individually.
+Then, in a second step, these paths are combined with the schema, and checked again for satisfiability.
+Each kind of unsatisfiable path is marked differently in the AST.each path is considered as a sequence of basic navigation steps possibly with qualifiers.
+The first step is analyzed.
+Then each additional step is successively appended to this initial step and the resulting path is analyzed in turn.
+This makes it possible to identify precisely where the error has been introduced in the path and remove them.\\ \forceindent Similarly we can detect toggle which is marked as DEAD TOGGLE in the toogle repository but still they are present in the code base but they have no impact on code flow.\\
 
@@
 \label{study-setup}
-In order to explore the feature toggle related smell we have searched for open source projects and found some projects with feature toggle implemented in those project.But we have choose Google Chome as our main code base because it has more then 5 years active development life cycle with feature toggle in it and it is released frequently.So there might be any issue with feature toggle which might not maintain properly.
+In order to explore the feature toggle related smell we have searched for open source projects and found some projects with feature toggle implemented in those project.
+But we have choose Google chromium as our main code base because it has more then 5 years active development life cycle with feature toggle in it and it has rapid released.
+So there might be any issue with feature toggle which might not notice properly.
+We have used Eclipse Plugin Development Environment(PDE) which is a Java based framework, it provides support for building source code analysis applications.
+And we have used Eclipse C++ Development Tooling (CDT) which is Eclipse variant to support development of C/C++ applications.
+This is where the C++ project will be loaded from google chromium source code on the test workbench.Our toggle smell detection algorithm is implemented in java.
 \section{Case Study}
@@
 
+\section{Our Approach}
+\label{Methodology and Implimentation}
+We have created a project named "tsd" which stands for toggle smell detector.
+This project is implemented in Java using the Eclipse Plugin development API.
+The solution is developed as an eclipse plugin, without user interface support.
+The hook to initiate the toggle smell detection is implemented using the eclipse plugin API.
+A toolbar button is placed in the test workbench which triggers the smell detection.
+This is handled through an event handler callback method which is invoked by the eclipse runtime.
+The solution will currently detect smells in a C++ project using the eclipse CDT API.\\\\ \setlength{\parindent}{1em}Each smell detector is implemented by a extending an abstract class which provides a skeletal implementation of the interface.
+The event handler callback function will invoke all the toggle smell detector classes in an order and will print the details of the detected smells in the eclipse development workbench console window.\setlength{\parindent}{1em}Abstract syntax tree of the eclipse CDT API is utilized for each smell detection algorithm.
+The visitor designed pattern is applied on each of the source file to detect potential toggle smells.
+Each detector has an customized implementation of the AST visitor which is tailor made to detect that particular toggle smell.
+This design gives the flexibility to extend when an user interface is developed for this solution in the future.
+Typically this gives an option to detect a particular type of toggle smell in a code base by selecting the desired type from the menu.
+This is similar to how JDeodorant eclipse plugin user interface which has separate menu options to trigger a smell detection on a project or element within a project.
+\section{Implementation Details And Algorithm}
+\label{Details}
+The smell detector requires following prior information to begin with\\
+\newline \textbf{Toggle method signature or function name:} Without this information the toggle smell detector could not search for the pattern of the method used to check the toggle usage.
+
+\subsection{Dead/Stable toggle detector}
+The algorithm to detect the dead and stable toggles remain the same. The detector expects a prior input from the user to provide with the list of toggle flags which became obsolete and stable. 
+\begin{itemize}
+  	\item The detector loads the list of stable or dead toggle flags into a mathematical Set data structure which stores string data type.
+  	\item For every file, the detector checks whether it is a C++ source unit and not a header file.
+  	\item For the C++ source file, an AST is constructed using the Eclipse CDT API.
+	\item The AST is then traversed using a custom visitor.
+	\item The visitor checks only for the conditional statements which has the toggle method function call.
+	\item The parameter of the toggle method is extracted from the AST.
+	\item The parameter is checked against the HashSet of strings which contain the dead or stable toggle flags.
+	\item If there is a match then the particular file, line number information is captured.
+	\item The locations where the dead/stable toggle flags are used in the code are stored in a data structure that is used for reporting the toggle smells.
+	\item The smell detector will report the smells that are observed when all source files are scanned.
+\end{itemize}
+\subsection{Nested Toggle detection}
+Nested toggle smell is a file level or a compilation unit level smell. The algorithm to detect the nested toggle is as follows:
+\begin{itemize}
+  	\item The smell detector get C++ source file from the project source roots.
+  	\item For every file AST is constructed using the eclipse CDT API.
+	\item An AST visitor is used to visit all the conditional branching statements (IF) for a source compilation unit.
+	\item The smell detector invokes an AST visitor through the AST reference.
+	\item The visitor checks only for the conditional statements which has the toggle method function call.
+If there is a toggle method invocation, then the corresponding ASTNode instance is stored in a Set data structure.
+	\item When a subsequent conditional statement is visited by the visitor, then the algorithm checks whether there is a parent IF conditional statement which encapsulates the current conditional statement.
+	\item If there exists a parent IF conditional statement then the smell detector captures the smell information into a separate data structure.
+	\item The smell detector class then consolidates all the smells from every compilation unit and store in another data structure to present for reporting the smells.
+	\item The report contains information of the toggle flag which is nested under another toggle flag. The line number and file path are presented.
+\end{itemize}
+\subsection{(Spaghetti) Toggle Smell Detection}
+Combinatorial toggle smell is a file level or a compilation unit level smell. The algorithm to detect the nested toggle is as follows:
+\begin{itemize}
+	\item The smell detector get C++ source file from the project source roots.
+	\item For every file AST is constructed using the eclipse CDT API.
+	\item An AST visitor is used to visit all the conditional branching statements (IF) for a source compilation unit.
+	\item The smell detector invokes an AST visitor through the AST reference.
+	\item The visitor checks only for the conditional statements which contains more than one conditional expression combined with logical AND or logical OR operators.
+These expressions are binary expressions.
+	\item Each operand of the binary expression is compared to see whether there is a toggle method invocation.
+	\item The algorithm has an recursive search function which takes the first statement and then keep searching all the expressions and extract all the arguments used in the invocation of the toggle method name.
+	\item If there are more than one conditional expression within the IF statement, then a potential combinatorial toggle smell is marked by the algorithm for presenting.
+	\item The smell detector class then consolidates all the smells from every compilation unit and store in another data structure to present for reporting the smells.
+	\item The report contains line number of the combinatorial toggle smell in the C++ compilation unit.
+The line number, list of toggle flags used in that statement along with the file path are presented in the report.
+\end{itemize}
+\subsection{Spread Toggle Smell Detection}
+The spread toggle smell is a project level smell which indicates that features are not isolated enough and might indicate high coupling in the modules.The algorithm to detect the spread toggle is as follows:
+\begin{itemize}
+	\item The smell detector get C++ source file from the project source roots.
+	\item For every file AST is constructed using the eclipse CDT API.
+	\item An AST visitor is used to visit all the conditional branching statements (IF) for a source compilation unit.
+	\item The smell detector invokes an AST visitor through the AST reference.
+	\item The visitor checks only for the conditional statements which has the toggle method function call.
+	\item If there is a toggle method invocation, then the method parameter is extracted and stored in a dictionary data structure with key as the parameter name and the value being the file path.
+The line number parameter is also recorded for reporting.
+	\item Once all the source files are scanned, the detector runs through the dictionary data structure to check the toggle flags which are used in more than one file.
+	\item The smell report is generated with all the toggle flags which are used in more than one file.
+The report includes the toggle flag name, the file and line number information where it is being used.
+\end{itemize}
+\section{Comparison with Alternate solutions}
+\label{Comparison with Alternate solutions}
+\subsection{Dead/Stable toggle detector}
+There are several alternate solutions that can be used to detect the dead/stable toggle smells in the source code.
+
+\forceindent 1. The search for a toggle flag could be accomplished using native operating system search commands like grep or find in Linux based systems.
+
+However such search would identify all the instances of the toggle flag, for example a text based tool might give a result of finding the search item which are present in non source files, code comments etc.
+
+\forceindent 2.
+Eclipse and other IDE provide search options similar to native operating system commands.
+This has the similar drawback as the native search tools as it might also provide search results from non source elements.
+
+\forceindent 3.
+Eclipse and other IDE provide search through references and call hierarchy.
+This option performs the search through the internal index maintained by the IDE which is much faster than scanning each file and using the AST parser.
+However a developer will  have to search repeatedly for each of the dead/stable toggle flags and note down the locations of their usages and perform refactoring later.
+\subsection{Nested Toggle detection}
+To search for the presence of nested toggle smell one, a developer could use one of the following methods
+
+	\forceindent 1.
+Search using native commands like find or grep.
+However going over the output of the grep command in order to identify the presence of nested toggle smell is very tedious and time consuming task.
+As the output may be large in case of a huge project code base.\\
+	\forceindent 2.
+The developer could also use IDE built-in capabilities to search for the instances where the toggle method is used within the source files.
+This gives the similar output as our smell detection algorithm, however the search does not indicate the smell, the developer has to manually introspect the source files to identify the nested toggle smell.
+
+	This search gives many instances of occurrences of the toggle method name even in the places where the nested toggle smell is not observed.
+So it is the developer responsibility to go over the source code to identify the nested toggle smells.
+\subsection{Combinatorial (Spaghetti) Toggle Smell Detection}
+1.Native OS commands
+\forceindent \begin{itemize}
+		\item Again comparing with native operating system search commands, a user to identify a spread toggles in a huge code base involves a tedious tasks of correlating the use of toggle flag and the file names.
+	\item The user has to search for the existence of each toggle flag and map it with the presence in the multiple source files.
+That means multiple search execution for each toggle flag that he/she is interested.
+	\item Searching for the occurrences of the toggle method name is even difficult as the search output will be large and it will be difficult to correlate a single toggle flag spread across multiple source files from the command output.
+\end{itemize}
+
+2. IDE Search
+\forceindent \begin{itemize}
+	\item Searching for variable references or method references using IDE capabilities as found in Eclipse IDE will also involves the tedious task of correlation to the user.
+	\item If searched for the variable references, then again the developer has to search the code for multiple variables.
+\end{itemize}
+
 \section{Results}
@@
 TODO
+
+\section{Limitations}
+\label{Limitation of our approach}
+There are some limitation in our approach. The limitation are given in details according to toggles smells.
+\subsection{Dead/Stable toggle}
+The limitations of our approach for dead toggle are follows:
+
+	1. The detector expects the input to be provided by user. This might be error prone.\\
+
+	2.
+If there is a temporary local variable used in the source file and then being used as an argument to the toggle method, then the detector will not trace the variable used and find/derive the actual value of the variable.
+The detector algorithm limits itself only on the token value of the argument rather than doing program analysis on the variable type and data flow.\\
+
+	3. The smell detector algorithm does not cross verify the toggle flag against an internal repository if any that is maintained within the target project.
+\subsection{Nested Toggle}
+The following are the limitations of the algorithm of detecting Nested Toggle:
+	1.
+If there are local or member variables used within the method or the class, the algorithm will not trace the variable to find the corresponding assigned value.
+It will use the parameter argument from the AST.
+This is current implementation limitation which can be fixed to understand the semantics of the argument and identify the actual value.
+	2. Current implementation will check only for the following variants of the nested toggles
+\begin{lstlisting}
+IF(ToggleMethod("FLAG1")) {
+	...
+	IF(ToggleMethod("FLAG2") {
+		…
+	}
+}
+
+OR
+
+IF(!ToggleMethod("FLAG1")) {
+	…
+	IF(ToggleMethod("FLAG2") {
+		…
+	}
+}\end{lstlisting}
+
+and the vice versa variant.
+It will not detect if there is a complex conditional expression if used within the conditional statement.
+The complex condition includes but not limited to logical AND, logical OR operators whose operands could be either the toggle method call or other expressions.
+
+For example the algorithm will not detect the following pattern as a nested toggle smell even though it qualifies for such smell
+\begin{lstlisting}
+IF(ToggleMethod("FLAG1") && ToggleMethod("FLAG2")) {
+	…
+
+	IF(ToggleMethod("FLAG3")) {
+		…
+	}
+
+}	
+	OR even the following pattern
+	IF(ToggleMethod("FLAG1") && someVar) {
+		…
+		IF(ToggleMethod("FLAG3")) {
+		…
+	}
+}
+\end{lstlisting}
+\subsection{Combinatorial (Spaghetti) Toggle}
+There is another class of spaghetti (Combinatorial) toggle code smell which involves having multiple toggle flags within a single class or single method within a class.
+Though this also pattern of toggle usage also qualifies for combinatorial toggle as it increases the test permutations and coverage complexity, our algorithm does not detect it at present.
+The implementation for the same is in progress and whose results will be published later in another publication.The following use cases are not detected by the solution:
+	1. Use of local variable or member variables of the class storing the output of the toggle method and being used in the conditional statement. As example below
+\begin{lstlisting}
+	bool flag1 = ToggleMethod("Flag1");
+	bool flag2 = ToggleMethod("Flag2");
+	bool flag3 = ToggleMethod("Flag3");
+
+	if(flag1 && flag2 || flag3) {
+		…
+	}
+\end{lstlisting}
+	This kind of usage pattern will not be detected by the algorithm in its present form.
+	\subsection{Spread Toggle}
+	As with limitations in the other toggle smell detection algorithms, the solution will not trace out the variables which contains the return value from the toggle method and being used in the conditional statement.
+
+Also use of toggle flags for other purposes without the invocation of the toggle method will not be checked by the algorithm as such usages might not indicate a potential toggle code smell.
+
+Also many a times few configuration toggle flags will be used throughout the project, though our solution detects this usage as a toggle spread, the solution could be improved to accept feedback from the developers and should improve the search criterias.
 

### 2015-12-06 paper/paper.tex
adding abstract

@@
 \usepackage{enumitem}
-\setlength{\parindent}{4em}
-\newcommand{\forceindent}{\leavevmode{\parindent=4em\indent}}
+
 \newcommand{\todo}[1]{\qquad\textcolor{red}{TODO: #1}\PackageWarning{TODO:}{#1!}}
@@
   breakatwhitespace=true,
-  tabsize=3
+  tabsize=1
 }
@@
 \begin{abstract}
-TODO
+Identifying code smell is the first step to re-factor a software system. 
+In Google Chrome developers use feature toggles to control their features 
+and keep developing on a single trunk. This paper investigates code smell 
+caused by improper use of feature toggles in Google Chrome that we call 
+as toggle smell. Using feature toggles to hide/unhide features is an old 
+concept but recently being practised in many software companies. Improper 
+use of toggles might cause code smell including duplicate code, dead code, 
+coupling and lack of cohesion. We classified the smells caused by toggles 
+in six different patterns Dead Toggles, Nested Toggles, Combinatorial (spaghetti) Toggles, 
+Mix of Compile-Time and Runtime Toggles, Legacy toggles and Spread Toggles. 
+We created a tool ``TSD'' as an Eclipse plug-in using Eclipse C++ Development Tooling (CDT) to identify these toggle 
+smells in major modules of Google Chrome source code. We found TODO 
+nested toggles smells, TODO spaghetti toggles and TODO spread toggles in ``chrome'' and ``base'' modules of Google Chrome.\\
 \end{abstract}
@@
 \begin{IEEEkeywords}
-Software Refactoring, Software Re-Engineering, Software Design, Feature Toggles, Code Smell, Technical Debt, Mining Repository
+Software Refactoring, Software Re-Engineering, Software Design, FeatureToggles, Code Smell, Technical Debt, Mining Repository
 \end{IEEEkeywords}
@@
 \label{related-works}
-Now a days continuous delivery of a software product is common in software industry.
+Continuous delivery of a software product is a recent trend in to develop software.
 In order to maintain the existing features and adding or removing new features in a software system is becoming the harder thing in terms of maintains.
-To keep track and handle the features in some software system toggling is used.In order to study about the code smells and feature toggle, we have studied many paper but four of them most influential.\\
-\forceindent Jens Knoop, Oliver Ruthing, Bernhard Steffen have worked on Partial Dead Code Elimination.
+To keep track and handle the features in some software system toggling is used.
+In order to study about the code smells and feature toggle, we have studied many paper but four of them most influential.\\
+
+Jens Knoop, Oliver Ruthing, Bernhard Steffen have worked on Partial Dead Code Elimination.
 They present an algorithm to eliminate partial dead code and to improve the speed of execution of program by moving the unnecessary variable assignment (Faint assignment) to the farthest location in the control flow graph, without changing the semantics of the program.
@@
 The dead assignments are identified using definition-use graphs.The delayability analysis is a technique to identify the location in the block of code to hoist a variable assignment.\\
-\forceindent Like their study we can identify the various taxonomies of toggle flag like \textbf{“INVALID TOGGLE”} and \textbf{“STABLE TOGGLE”} usages and smells  in a code base.
+
+Like their study we can identify the various taxonomies of toggle flag like \textbf{“INVALID TOGGLE”} and \textbf{“STABLE TOGGLE”} usages and smells  in a code base.
 We could leverage their techniques to see the impact of the toggle flag in the further parts of the program either in same program artifact or other artifacts so as to identify the way for their elimination.
-We would like to know the impacts of removing certain variable assignments (in our case toggle flags) and how it will impact the control flow structures.\\\\
-\forceindent Tiago Pessoa and his colleagues develop an Eclipse Plugin to support Code Smells using Binary Logistic Regression Model.
+We would like to know the impacts of removing certain variable assignments (in our case toggle flags) and how it will impact the control flow structures.\\
+
+Tiago Pessoa and his colleagues develop an Eclipse Plugin to support Code Smells using Binary Logistic Regression Model.
 Their tool is for detecting code smells using BLRM by using the heuristic of expert knowledge to calibrate the model.
@@
 McCabe Cyclomatic Complexity}\\
-\forceindent The authors have used binary logistic regression model in their plugin development to determine the outcome of a code smell.
+
+The authors have used binary logistic regression model in their plug-in development to determine the outcome of a code smell.
 We could leverage this technique to create a statistical model to determine whether there is a toggle related code smell by collecting data from the source code and using heuristic knowledge about the toggle.
-For example to determine whether a code block covered by a  “STABLE TOGGLE” is a potential candidate for refactoring the BLR can be trained with the meta data such as time the toggle was introduced, number of state changes during development, number of state changes in the field, number of bugs etc and the BLR can come with the prediction to indicate potential refactorings.\\\\
-\forceindent Gail C.
+For example to determine whether a code block covered by a  “STABLE TOGGLE” is a potential candidate for refactoring the BLR can be trained with the meta data such as time the toggle was introduced, number of state changes during development, number of state changes in the field, number of bugs etc and the BLR can come with the prediction to indicate potential refactorings.\\
+
+Gail C.
 Murphy and his colleagues investigate about the separation of features in existing code.For the the purpose of the investigation they conducted an exploratory study in the context of two existing systems: \textbf{gnu.regexp and jFTPd}.
@@
 How the tool like Hyper/J tool could help to identify the code in an existing set of class files contributes to a particular dimension, and within a dimension to particular concerns.\\
+
 They considered two common kinds of feature encodings in two existing Java systems.
@@
 They wanted to separate these features that were originally tangled in a single method so as to produce a system that might support, for instance, only multi-line matches.\\
-\forceindent In our research objective we have to classify the code smells related to the usage of features toggles.
+
+In our research objective we have to classify the code smells related to the usage of features toggles.
 One such code smell is to identify the distribution of the same toggles flag among various sources files, we have named this as “TOGGLE SPREAD”.
@@
 This study is used to identify the features from the source code using Aspect oriented programming.\\
-\newline \forceindent Pierre Genevès and Nabil Layaïda analysis, how to detect and remove dead code from Xquery programs.
+
+Pierre Genevès and Nabil Layaïda analysis, how to detect and remove dead code from Xquery programs.
 They propose a technique for performing static basic dead-code analysis and eliminate the dead code from an XQuery program.
@@
 In the path-error detection they gave a scema as input to an XQuery program and For each XPath expression occurring in XQuery program, they just check that it is meaningful or not with respect to the constraints described in scema.
-If navigational information contained in a given path contradicts the constraints described in Scema then the path will always return an empty sequence of nodes.
+If navigational information contained in a given path contradicts the constraints described in Scema then the path will always return an empty sequence of nodes.\\
+
 All XQuery instructions that depend on that path are dead code and maybe they should remove.
@@
 Then each additional step is successively appended to this initial step and the resulting path is analyzed in turn.
-This makes it possible to identify precisely where the error has been introduced in the path and remove them.\\ \forceindent Similarly we can detect toggle which is marked as DEAD TOGGLE in the toogle repository but still they are present in the code base but they have no impact on code flow.\\
+This makes it possible to identify precisely where the error has been introduced in the path and remove them.
+Similarly we can detect toggle which is marked as DEAD TOGGLE in the toogle repository but still they are present in the code base but they have no impact on code flow.\\
 
@@
 This is handled through an event handler callback method which is invoked by the eclipse runtime.
-The solution will currently detect smells in a C++ project using the eclipse CDT API.\\\\ \setlength{\parindent}{1em}Each smell detector is implemented by a extending an abstract class which provides a skeletal implementation of the interface.
-The event handler callback function will invoke all the toggle smell detector classes in an order and will print the details of the detected smells in the eclipse development workbench console window.\setlength{\parindent}{1em}Abstract syntax tree of the eclipse CDT API is utilized for each smell detection algorithm.
+The solution will currently detect smells in a C++ project using the eclipse CDT API.\\
+
+Each smell detector is implemented by a extending an abstract class which provides a skeletal implementation of the interface.
+The event handler callback function will invoke all the toggle smell detector classes in an order and will print the details of the detected smells in the eclipse development workbench console window.\\
+
+Abstract syntax tree of the eclipse CDT API is utilized for each smell detection algorithm.
 The visitor designed pattern is applied on each of the source file to detect potential toggle smells.
@@
 \end{itemize}
-\section{Comparison with Alternate solutions}
-\label{Comparison with Alternate solutions}
-\subsection{Dead/Stable toggle detector}
+\section{Comparison with Alternate Solutions}
+\label{comparison-with-alternate-solutions}
+\subsection{Dead Toggle Detector}
 There are several alternate solutions that can be used to detect the dead/stable toggle smells in the source code.
 
-\forceindent 1. The search for a toggle flag could be accomplished using native operating system search commands like grep or find in Linux based systems.
+\begin{enumerate}
+\item{The search for a toggle flag could be accomplished using native operating system search commands like grep or find in Linux based systems.
+However such search would identify all the instances of the toggle flag, for example a text based tool might give a result of finding the search item which are present in non source files, code comments etc.}
 
-However such search would identify all the instances of the toggle flag, for example a text based tool might give a result of finding the search item which are present in non source files, code comments etc.
+\item{Eclipse and other IDE provide search options similar to native operating system commands.
+This has the similar drawback as the native search tools as it might also provide search results from non source elements.}
 
-\forceindent 2.
-Eclipse and other IDE provide search options similar to native operating system commands.
-This has the similar drawback as the native search tools as it might also provide search results from non source elements.
+\item{Eclipse and other IDE provide search through references and call hierarchy.
+This option performs the search through the internal index maintained by the IDE which is much faster than scanning each file and using the AST parser.
+However a developer will  have to search repeatedly for each of the dead/stable toggle flags and note down the locations of their usages and perform refactoring later.}
+\end{enumerate}
 
-\forceindent 3.
-Eclipse and other IDE provide search through references and call hierarchy.
-This option performs the search through the internal index maintained by the IDE which is much faster than scanning each file and using the AST parser.
-However a developer will  have to search repeatedly for each of the dead/stable toggle flags and note down the locations of their usages and perform refactoring later.
 \subsection{Nested Toggle detection}
@@
 
-	\forceindent 1.
-Search using native commands like find or grep.
+\begin{enumerate}
+\item{Search using native commands like find or grep.
 However going over the output of the grep command in order to identify the presence of nested toggle smell is very tedious and time consuming task.
-As the output may be large in case of a huge project code base.\\
-	\forceindent 2.
-The developer could also use IDE built-in capabilities to search for the instances where the toggle method is used within the source files.
-This gives the similar output as our smell detection algorithm, however the search does not indicate the smell, the developer has to manually introspect the source files to identify the nested toggle smell.
+As the output may be large in case of a huge project code base.}
+\item{The developer could also use IDE built-in capabilities to search for the instances where the toggle method is used within the source files.
+This gives the similar output as our smell detection algorithm, however the search does not indicate the smell, the developer has to manually introspect the source files to identify the nested toggle smell.}\\
+\end{enumerate}
 
@@
 So it is the developer responsibility to go over the source code to identify the nested toggle smells.
+
 \subsection{Combinatorial (Spaghetti) Toggle Smell Detection}
-1.Native OS commands
-\forceindent \begin{itemize}
+
+\begin{enumerate}
+\item{Native OS commands:
+
+\begin{itemize}
 \item Again comparing with native operating system search commands, a user to identify a spread toggles in a huge code base involves a tedious tasks of correlating the use of toggle flag and the file names.
@@
 \end{itemize}
+}
 
-2. IDE Search
-\forceindent \begin{itemize}
+\item{IDE Search:
+\begin{itemize}
 \item Searching for variable references or method references using IDE capabilities as found in Eclipse IDE will also involves the tedious task of correlation to the user.
@@
 \end{itemize}
+}
+\end{enumerate}
 
@@
 There are some limitation in our approach. The limitation are given in details according to toggles smells.
-\subsection{Dead/Stable toggle}
+\subsection{Dead toggle}
 The limitations of our approach for dead toggle are follows:
 
-	1. The detector expects the input to be provided by user. This might be error prone.\\
+\begin{enumerate}
+\item{The detector expects the input to be provided by user. This might be error prone.}
 
-	2.
-If there is a temporary local variable used in the source file and then being used as an argument to the toggle method, then the detector will not trace the variable used and find/derive the actual value of the variable.
-The detector algorithm limits itself only on the token value of the argument rather than doing program analysis on the variable type and data flow.\\
+\item{If there is a temporary local variable used in the source file and then being used as an argument to the toggle method, then the detector will not trace the variable used and find/derive the actual value of the variable.
+The detector algorithm limits itself only on the token value of the argument rather than doing program analysis on the variable type and data flow.}
 
-	3. The smell detector algorithm does not cross verify the toggle flag against an internal repository if any that is maintained within the target project.
+\item{The smell detector algorithm does not cross verify the toggle flag against an internal repository if any that is maintained within the target project.}
+\end{enumerate}
+
 \subsection{Nested Toggle}
 The following are the limitations of the algorithm of detecting Nested Toggle:
-	1.
-If there are local or member variables used within the method or the class, the algorithm will not trace the variable to find the corresponding assigned value.
+\begin{enumerate}
+\item{If there are local or member variables used within the method or the class, the algorithm will not trace the variable to find the corresponding assigned value.
 It will use the parameter argument from the AST.
-This is current implementation limitation which can be fixed to understand the semantics of the argument and identify the actual value.
-	2. Current implementation will check only for the following variants of the nested toggles
+This is current implementation limitation which can be fixed to understand the semantics of the argument and identify the actual value.}
+\item{Current implementation will check only for the following variants of the nested toggles
+
 \begin{lstlisting}
@@
 \end{lstlisting}
+}
+\end{enumerate}
+
 \subsection{Combinatorial (Spaghetti) Toggle}

### 2015-12-06 src/edu/concordia/tsd/util/DirectoryPathFinder.java
All all utility scripts for the generate the XML file for .cProject and counting all the CPP files into the source file

@@ -1,15 +1,19 @@
 package edu.concordia.tsd.util;
 
 import java.io.File;
+import java.io.FileNotFoundException;
+import java.io.FilenameFilter;
+import java.io.PrintWriter;
 import java.util.ArrayList;
+import java.util.Arrays;
 import java.util.List;
 
 public class DirectoryPathFinder {
 	
 	// Need to write generate the XML file with the corresponding paths 
 
-	private final String PATH = "/Users/hitman4r44/Documents/Google_chrome_code/src/directoryTesting";
-	List<String> directoryPathList = new ArrayList<String>();
+	private final String PATH = "/Users/hitman4r44/Documents/Google_chrome_code/src/base";
+	static List<String> directoryPathList = new ArrayList<String>();
 
 	public void walk(String path) {
 
@@ -22,16 +26,84 @@ public class DirectoryPathFinder {
 		for (File f : list) {
 			if (f.isDirectory()) {
 				walk(f.getAbsolutePath());
-				directoryPathList.add(f.getAbsoluteFile().toString().replace(PATH, ""));
+				directoryPathList.add(f.getAbsoluteFile().toString().replace(PATH+"/", ""));
 			}
 		}
 	}
+	
+	private static String[] getAllDirectoriesName(File file) {
 
-	public static void main(String[] args) {
+		String[] directories = file.list(new FilenameFilter() {
+			@Override
+			public boolean accept(File current, String name) {
+				return new File(current, name).isDirectory();
+			}
+		});
+		System.out.println(Arrays.toString(directories));
+
+		return directories;
+	}
+
+	public static void main(String[] args) throws FileNotFoundException {
 
 		DirectoryPathFinder pathFinder = new DirectoryPathFinder();
 		pathFinder.walk(pathFinder.PATH);
+		
 		printTheList(pathFinder.directoryPathList);
+		
+		String[] allParentDirectory = getAllDirectoriesName(new File (pathFinder.PATH));
+		
+		pathFinder.generateTheMiddleXMLfile(allParentDirectory);
+		
+		//Merge all files into one file
+		String sourceFile1Path = "resources/XMLFirstParagraph.txt";
+		String sourceFile2Path = "resources/XMLMiddleParagraph.txt";
+		String sourceFile3Path = "resources/XMLLastParagraph.txt";
[…]

### 2015-12-06 src/edu/concordia/tsd/util/MergerFiles.java

@@ -1,0 +1,69 @@
+package edu.concordia.tsd.util;
+
+import java.io.BufferedReader;
+import java.io.BufferedWriter;
+import java.io.File;
+import java.io.FileInputStream;
+import java.io.FileWriter;
+import java.io.IOException;
+import java.io.InputStreamReader;
+
+public class MergerFiles {
+
+	public static void main(String[] args) {
+		
+		String sourceFile1Path = "resources/XMLFirstParagraph.txt";
+		String sourceFile2Path = "resources/XMLMiddleParagraph.txt";
+		String sourceFile3Path = "resources/XMLLastParagraph.txt";
+
+		String mergedFilePath = "resources/.cproject";
+
+		File[] files = new File[3];
+		
+		files[0] = new File(sourceFile1Path);
+		files[1] = new File(sourceFile2Path);
+		files[2] = new File(sourceFile3Path);
+
+		File mergedFile = new File(mergedFilePath);
+
+		mergeFiles(files, mergedFile);
+	}
+
+	public static void mergeFiles(File[] files, File mergedFile) {
+
+		FileWriter fstream = null;
+		BufferedWriter out = null;
+		try {
+			fstream = new FileWriter(mergedFile, true);
+			out = new BufferedWriter(fstream);
+		} catch (IOException e1) {
+			e1.printStackTrace();
+		}
+
+		for (File f : files) {
+			System.out.println("merging: " + f.getName());
+			FileInputStream fis;
+			try {
+				fis = new FileInputStream(f);
+				BufferedReader in = new BufferedReader(new InputStreamReader(fis));
+
+				String aLine;
+				while ((aLine = in.readLine()) != null) {
+					out.write(aLine);
+					out.newLine();
+				}
+
+				in.close();
+			} catch (IOException e) {
+				e.printStackTrace();
+			}
+		}
+
+		try {
+			out.close();
+		} catch (IOException e) {
+			e.printStackTrace();
+		}
+
+	}
+}

### 2015-12-06 paper/paper.tex
writing paper

@@
 \section{Introduction}
+TODO\\
 
@@
 \label{related-works}
-Continuous delivery of a software product is a recent trend in to develop software.
+Continuous delivery of a software product is a recent trend in to develop software\cite{Del2006Continuous}.
 In order to maintain the existing features and adding or removing new features in a software system is becoming the harder thing in terms of maintains.
@@
 
-Jens Knoop, Oliver Ruthing, Bernhard Steffen have worked on Partial Dead Code Elimination.
+Jens Knoop, Oliver Ruthing, Bernhard Steffen~\cite{knoop1994partial} have worked on Partial Dead Code Elimination.
 They present an algorithm to eliminate partial dead code and to improve the speed of execution of program by moving the unnecessary variable assignment (Faint assignment) to the farthest location in the control flow graph, without changing the semantics of the program.
@@
 
-Tiago Pessoa and his colleagues develop an Eclipse Plugin to support Code Smells using Binary Logistic Regression Model.
+Tiago Pessoa and his colleagues~\cite{pessoa2012eclipse} develop an Eclipse Plugin to support Code Smells using Binary Logistic Regression Model.
 Their tool is for detecting code smells using BLRM by using the heuristic of expert knowledge to calibrate the model.
@@
 The binary logistic regression with dependent variable having two values (either code smell present or absent) has been used to detect the probability of code smell.
-The BLR is calibration is done using the statistical tools like R or SPSS and JRI (Java R Inteface) is used to interface with R language from the eclipse plugin.
+The BLR is calibration is done using the statistical tools like R or SPSS and JRI (Java R Inteface) isWe classified toggle smells in different classes based on their usage in the source code.
+Before that we studied different types of feature toggles available in Google Chrome.
+
+\subsection{Compile Time toggles}
+The first set of usage patterns we descriptively belongs to the compile 
+time toggles. Here changing the toggle value requires modifying the source 
+code and generating a new binary to enable or disable a particular feature 
+for testing or release. The usage also relies upon the support in the 
+programming language for managing enumerations.
+
+Even though the patterns are not complex, they are subtle for small projects (like capstone or start-ups) in order to manage feature dependencies and 
+avoid feature branching. Another benefit of compile time toggles is, when 
+cleaning up the toggle code at the end of toggle life. The location of the 
+changes could be easily identified by commenting out the field containing the toggle flag.
+
+\subsection{Constants Variables}
+In this pattern the value of the toggle state of a feature is managed through a constant variable declared in the program.
+In languages like C/C++, const modifiers will be used to inform that state of the feature flags will not change throughout the lifetime of the program.
+In Java final modifiers will be used.
+The data type of the variable could be a boolean or integer.\\
+
+For example,  in Java, the constants could be declared in a final static class and used in all source files using static imports.\\
+
+\begin{lstlisting}
+public final class ToggleStates {
+    public static final boolean IS\_FEATURE1_ENABLED = true;
+    public static final boolean IS\_FEATURE2_ENABLED = true;
+    ... ...
+}
+\end{lstlisting}
+
+\subsection{Enumerations Interface}
+In Java there is a support to manage set of states through “enum” interface which is much richer when compared to languages like C, C++ (C++11 has similar support).
+The enum can implement interfaces and provide some flexibility in defining the toggle API (Togglz framework uses this approach) to use rather than using the constant variables directly.\\
+
+public enum ToggleFlags
+{
+    FEATURE1(false),
+    FEATURE2(true),
+    FEATURE3(false);\\
+
+    private boolean state;
+    private ToggleFlags(boolean state) { this.state = state; }\\
+
+    public boolean isEnabled() { return this.state; }
+}\\
+
+The client code can directly use this \textit{enum} class method as below ``ToggleFlags.FEATURE1.isEnabled()'' which looks much cleaner in code when compared to accessing the values through constant variables.
+
+\subsection{Compile-Time Macros}
+ used to interface with R language from the eclipse plugin.
 The plugin operates in two different modes (local and remote).
@@
 Gail C.
-Murphy and his colleagues investigate about the separation of features in existing code.For the the purpose of the investigation they conducted an exploratory study in the context of two existing systems: \textbf{gnu.regexp and jFTPd}.
+Murphy et.
+al.~\cite{murphy2001separating} investigate about the separation of features in existing code.For the the purpose of the investigation they conducted an exploratory study in the context of two existing systems: \textbf{gnu.regexp and jFTPd}.
 They have proposed two methodologies to separate out the features from the source code which are either tangled within a single method or across several classes.
@@
 
-Pierre Genevès and Nabil Layaïda analysis, how to detect and remove dead code from Xquery programs.
+Pierre Genevès and Nabil Layaïda~\cite{geneves2010eliminating} studied how to detect and remove dead code from Xquery programs.
 They propose a technique for performing static basic dead-code analysis and eliminate the dead code from an XQuery program.
@@
 \label{results}
-TODO: Answer the research questions
+We classified toggle smells in different classes based on their usage in 
+the source code. Before that we studied different types of feature toggles 
+available in Google Chrome.
+
+\subsection{Compile Time toggles}
+The first set of usage patterns we descriptively belongs to the compile 
+time toggles. Here changing the toggle value requires modifying the source 
+code and generating a new binary to enable or disable a particular feature 
+for testing or release. The usage also relies upon the support in the 
+programming language for managing enumerations.
+
+Even though the patterns are not complex, they are subtle for small projects (like capstone or startups) in order to manage feature dependencies and 
+avoid feature branching. Another benefit of compile time toggles is, when 
+cleaning up the toggle code at the end of toggle life. The location of the 
+changes could be easily identified by commenting out the field containing the toggle flag.
+
+\subsection{Constants and Variables}
+In this pattern the value of the toggle state of a feature is managed through a constant variable declared in the program.
+In languages like C/C++, const modifiers will be used to inform that state of the feature flags will not change throughout the lifetime of the program.
+In Java final modifiers will be used.
+The data type of the variable could be a boolean or integer.\\
+
+For example,  in Java, the constants could be declared in a final static class and used in all source files using static imports.\\
+
+\begin{lstlisting}
+public final class ToggleStates {
+    public static final boolean IS_FEATURE1_ENABLED = true;
+    public static final boolean IS_FEATURE2_ENABLED = true;
+    ... ...
+}
+\end{lstlisting}
+
+\subsection{Enumerations}
+In Java there is a support to manage set of states through “enum” interface which is much richer when compared to languages like C, C++ (C++11 has similar support).
+The enum can implement interfaces and provide some flexibility in defining the toggle API (Togglz framework uses this approach) to use rather than using the constant variables directly.\\
+
+\begin{lstlisting}
+public enum ToggleFlags
+{
+    FEATURE1(false),
+    FEATURE2(true),
+    FEATURE3(false);
+
+    private boolean state;
+    private ToggleFlags(boolean state) { this.state = state; }
+
+    public boolean isEnabled() { return this.state; }
+}
+\end{lstlisting}
+
+The client code can directly use this \textit{enum} class method as below ``ToggleFlags.FEATURE1.isEnabled()'' which looks much cleaner in code when compared to accessing the values through constant variables.
+
+\subsection{Compile-Time Macros}
 
@@
 This is similar to how JDeodorant eclipse plugin user interface which has separate menu options to trigger a smell detection on a project or element within a project.
+
 \section{Implementation Details And Algorithm}
 \label{Details}
-The smell detector requires following prior information to begin with\\
-\newline \textbf{Toggle method signature or function name:} Without this information the toggle smell detector could not search for the pattern of the method used to check the toggle usage.
+The smell detector requires following prior information to begin with:
 
-\subsection{Dead/Stable toggle detector}
+\textbf{Toggle method signature or function name:} Without this information the toggle smell detector could not search for the pattern of the method used to check the toggle usage.
+
+\subsection{Dead Toggle Smell Detector}
 The algorithm to detect the dead and stable toggles remain the same. The detector expects a prior input from the user to provide with the list of toggle flags which became obsolete and stable. 
@@
 \label{comparison-with-alternate-solutions}
-\subsection{Dead Toggle Detector}
+\subsection{Dead Toggle Detection}
 There are several alternate solutions that can be used to detect the dead/stable toggle smells in the source code.

### 2015-12-06 paper/paper.tex
writing intro

@@
 \section{Introduction}
-TODO\\
+Identifying code smell is a vital task for better refactoring.
+Large amount of effort could be saved if a bad smell in a software project is ditected properly.
+Refactoring becomes more costly when there is lack of proper development documentations.
+Feature oriented Model Driven Development allows us develop software system to grow up in a feature oriented way that dictates the features to be distinguishable and understandable.
+To develop features in an isolated way while developing on a single trunk major software companies including Google~\cite{ChromeRepidRelease}, Facebook~\cite{Rossi2014Google} and Netflix use feature toggles to enable or disable a feature from the enduser access.
 

### 2015-12-07 src/edu/concordia/tsd/smells/deadtoggle/DeadToggleFlagVisitorVisitor.java
Dead toggle detector fix.

@@ -69,7 +69,7 @@ public class DeadToggleFlagVisitorVisitor extends ASTVisitor {
 				// is mingled with other conditons.
 			}
 		}
-		return super.visit(statement);
+		return PROCESS_CONTINUE;
 	}
 	
 	public Map<String, Set<Integer>> getToggleFlagsUsedInThisTU() {

### 2015-12-07 src/edu/concordia/tsd/smells/deadtoggle/DeadToggleSmellDetector.java

@@ -10,6 +10,8 @@ import org.eclipse.cdt.core.dom.ast.IASTFunctionCallExpression;
 import org.eclipse.cdt.core.dom.ast.IASTInitializerClause;
 import org.eclipse.cdt.core.dom.ast.IASTStatement;
 import org.eclipse.cdt.core.dom.ast.IASTTranslationUnit;
+import org.eclipse.cdt.core.dom.ast.cpp.ICPPASTBinaryExpression;
+import org.eclipse.cdt.core.dom.ast.cpp.ICPPASTFunctionCallExpression;
 import org.eclipse.cdt.core.dom.ast.cpp.ICPPASTIfStatement;
 import org.eclipse.cdt.core.dom.ast.cpp.ICPPASTUnaryExpression;
 import org.eclipse.cdt.core.model.ITranslationUnit;
@@ -78,9 +80,33 @@ public class DeadToggleSmellDetector extends AbstractSmellDetector {
 				if (conditionalExpr != null && conditionalExpr instanceof IASTFunctionCallExpression
 						&& conditionalExpr.getRawSignature().contains(toggleMethodName)) {
 					fcexpr = (IASTFunctionCallExpression) conditionalExpr;
+
+					if (fcexpr != null) {
+						checkDeadToggleSmell(fcexpr);
+					}
+
 				} else if (conditionalExpr instanceof IASTBinaryExpression) {
 					// This is the case where the function call expression
 					// is mingled with other conditions.
+
+					ICPPASTBinaryExpression cppASTBinaryExpression = (ICPPASTBinaryExpression) conditionalExpr;
+
+					Set<String> allToggleFlagsUsed = getAllToggleFlags(cppASTBinaryExpression, new HashSet<String>());
+					allToggleFlagsUsed.remove(null);
+
+					for (String toggleFlagUsed : allToggleFlagsUsed) {
+						for (String deadToggleFlagFromRepo : deadToggles) {
+							if (deadToggleFlagFromRepo.contains(toggleFlagUsed)) {
+								Set<ToggleContext> set = new HashSet<ToggleContext>();
+								ToggleContext tc = new ToggleContext(toggleFlagUsed);
+								tc.addFileAndLocation(cppASTBinaryExpression.getContainingFilename(),
+										cppASTBinaryExpression.getFileLocation().getStartingLineNumber());
+								set.add(tc);
+								toggleSmells.add(new ToggleSmell(ToggleSmellType.DEAD_TOGGLE, set));
+							}
+						}
+					}
+
[…]

### 2015-12-07 paper/paper.tex
writing introduction

--- 2015-12-06 paper/paper.tex
@@
 \section{Introduction}
-TODO\\
+Identifying code smell is a vital task for better re-factoring.
+Large amount of effort could be saved if a bad smell in a software project is detected properly.
+Re-factoring becomes more costly when there is lack of proper development documentations.
+Feature oriented Model Driven Development allows us develop software system to grow up in a feature oriented way that dictates the features to be distinguishable and understandable.
+To develop features in an isolated way while developing on a single trunk major software companies including Google~\cite{ChromeRepidRelease}, Facebook~\cite{Rossi2014Google} and Netflix use feature toggles to enable or disable a feature from the end-user access.
+However, improper use of feature toggles is a bad practice~\cite{Fowler2010FeatureToggle}.
+Feature toggles hide feature
+related code blocks until the feature is ready to publish. Once the 
+development of a feature is done and published but still the toggle is 
+left in the code, the blocked code becomes a dead code which is a technical 
+debt.\\
+
+Feature toggle is a variable used in an ``\textit{if}'' statement to control the 
+features under development. Source code, related to a particular feature executes 
+based on the value of a toggle or the presence/absence of the toggle itself. 
+We found in Google Chrome, that they are using feature toggles to manage their 
+features during development or even during testing. Some feature toggles are 
+being used to allow end-users flip the behaviour of certain feature of the browser.\\
+
+Commonly known code smells such as long methods, code clone, 
+god class, state-checking etc.~\cite{marticorena2006extending} make the 
+code hard to understand, error-prone and unmanageable for further enhancement. 
+Besides the known taxonomy of code smells, toggle smells could also be joined 
+in that taxonomy as considerable technical debts that need to be detected 
+and re-factored for the further improvement of the software.
+\\
 

### 2015-12-07 paper/paper.tex
writing intro, adding figure

@@
 being used to allow end-users flip the behaviour of certain feature of the browser.\\
+
+They use feature toggle to manage the features during development as well as 
+in testing and canary phase.
+
+Chrome is a popular, large open source project that has been using feature toggles for more than five years and that we use as case study in this paper. 
+Instead of having a single configuration file for toggles, Chrome has 
+multiple “switch files” representing toggleable sets of related features. 
+In Fig~\ref{fig:switch-sets} we can see few of the switch-set files 
+in Chrome containing toggles for their respective modules. 
+We can see switch files for features related to how content is 
+displayed in Chrome (content\_switches.cc) or to testing of GPU 
+(test\_switches.cc).
+\begin{figure}
+\includegraphics[height=0.5in,width=3.5in]{figure/switches.png}
+\caption{Toggle set / Switch set files in Chrome source code.}
+\label{fig:switch-sets}
+\end{figure}
+Each switch file contains a set of feature toggles that can
+be enabled or disabled. In Chrome, feature toggles are strings
+that can be set or unset. For example, Fig.~\ref{fig:content-toggles} 
+shows that the
+feature toggle kDisableFlashFullscreen3d is being set by
+giving it the value “disable-flash-fullscreen-3d”. This disables
+the feature that renders graphics in 3D when flash content is
+presented full-screen. Advanced users might use this toggle
+to improve performance~\cite{kDisableFlashFullscreen3d}.\\
+\begin{figure}
+\includegraphics[height=0.5in,width=3.5in]{figure/toggleassigned.png}
+\caption{Example toggles inside content\_switches.cc}
+\label{fig:content-toggles}
+\end{figure}
+
+While developers are working on a feature, 
+toggles are used in an if condition to let this feature
+turn on/off. In Google Chrome this is done by adding a toggle 
+or removing it from the switch set or feature set file. 
+For the above example of kDisableFlashFullscreen3d, 
+Fig.~\ref{fig:toggle-use} is showing us that the feature toggle is 
+being used in an if statement and if it is set it will not allow the 
+rest of the code in the function to be executed, which enables 3D 
+flash-fullscreen. That means the feature 3D flash-fullscreen has been 
+disabled by turning this toggle on.\\
+\begin{figure}
+\includegraphics[height=2in,width=3.5in]{figure/toggle-use.png}
+\caption{Example of use of toggle}
+\label{fig:toggle-use}
+\end{figure}
 

### 2015-12-07 paper/paper.tex
add the benifit of our algorithm for detecting ever file or os search

@@
 The enum can implement interfaces and provide some flexibility in defining the toggle API (Togglz framework uses this approach) to use rather than using the constant variables directly.\\
-
+\begin{lstlisting}
 public enum ToggleFlags
@@
     FEATURE2(true),
-    FEATURE3(false);\\
+    FEATURE3(false);
 
     private boolean state;
-    private ToggleFlags(boolean state) { this.state = state; }\\
+    private ToggleFlags(boolean state) { 				this.state = state; 
+    }
 
-    public boolean isEnabled() { return this.state; }
-}\\
+    public boolean isEnabled() { 
+    	return 	this.state; 
+    }
+}
+\end{lstlisting}
 
@@
 
+\textbf{Advantages of our approach:}
+
+Our approach to detect the toggle smells uses the abstract syntax trees from the eclipse CDT API.
+This makes the present solution extensible for future enhancements to suggest or perform automated or semi-automated refactorings to eliminate the dead/stable toggle from the target system.
+
+Our solution could also be extended to do a software repository mining to identify the potential stable and dead toggle flags used in the project.
+The solution could then present the list of identified dead/stable toggles and present it to the developer and upon his/her confirmation could act on the detection of dead/stable toggle smells.
+
+This way the solution does not expect manual input from the user.
+
 \subsection{Nested Toggle detection}
@@
 
+\textbf{Advantages of our approach: }
+
+Presenting a solution as an plugin within an IDE like eclipse facilitates the developers to quickly navigate to the file where the smell is found.
+Our solution results only the places where the nested toggle smell is observed ignoring other occurrences where the toggle method name is called.
+So the solutions presents more narrowed down results which saves time of the developer.
+
+As of today we are not aware of a search filter which can customize the search results such as find two or more occurrences of the invocation of the toggle method name within same class or same method.
+
 This search gives many instances of occurrences of the toggle method name even in the places where the nested toggle smell is not observed.
@@
 
-\subsection{Combinatorial (Spaghetti) Toggle Smell Detection}
+\subsection{Spread Toggle Smell Detection}
 
@@
 \end{enumerate}
+
+\textbf{Advantages of our solution}
+
+Our solution has an upper hand when compared with the manual searching through os commands or IDE search options might result in a large data set to correlate, compare and come to a conclusion of potential toggle smell.
+
+Our solution presents the toggle flag name, file path and low level details like line number which saves lot of time for the developers to identify this toggle smell.
 

### 2015-12-07 paper/paper.tex
remove the copy thing and added someting in code smells sections

@@
 \begin{document}
-\title{Togglge Smell Detection in Google Chrome}
+\title{Toggle Smell Detection in Google Chrome}
 \author{
@@
 The binary logistic regression with dependent variable having two values (either code smell present or absent) has been used to detect the probability of code smell.
-The BLR is calibration is done using the statistical tools like R or SPSS and JRI (Java R Inteface) isWe classified toggle smells in different classes based on their usage in the source code.
-Before that we studied different types of feature toggles available in Google Chrome.
-
-\subsection{Compile Time toggles}
-The first set of usage patterns we descriptively belongs to the compile 
-time toggles. Here changing the toggle value requires modifying the source 
-code and generating a new binary to enable or disable a particular feature 
-for testing or release. The usage also relies upon the support in the 
-programming language for managing enumerations.
-
-Even though the patterns are not complex, they are subtle for small projects (like capstone or start-ups) in order to manage feature dependencies and 
-avoid feature branching. Another benefit of compile time toggles is, when 
-cleaning up the toggle code at the end of toggle life. The location of the 
-changes could be easily identified by commenting out the field containing the toggle flag.
-
-\subsection{Constants Variables}
-In this pattern the value of the toggle state of a feature is managed through a constant variable declared in the program.
-In languages like C/C++, const modifiers will be used to inform that state of the feature flags will not change throughout the lifetime of the program.
-In Java final modifiers will be used.
-The data type of the variable could be a boolean or integer.\\
-
-For example,  in Java, the constants could be declared in a final static class and used in all source files using static imports.\\
-
-\begin{lstlisting}
-public final class ToggleStates {
-    public static final boolean IS\_FEATURE1_ENABLED = true;
-    public static final boolean IS\_FEATURE2_ENABLED = true;
-    ... ...
-}
-\end{lstlisting}
-
-\subsection{Enumerations Interface}
-In Java there is a support to manage set of states through “enum” interface which is much richer when compared to languages like C, C++ (C++11 has similar support).
-The enum can implement interfaces and provide some flexibility in defining the toggle API (Togglz framework uses this approach) to use rather than using the constant variables directly.\\
-\begin{lstlisting}
-public enum ToggleFlags
-{
-    FEATURE1(false),
-    FEATURE2(true),
-    FEATURE3(false);
-
-    private boolean state;
-    private ToggleFlags(boolean state) { 				this.state = state; 
-    }
-
-    public boolean isEnabled() { 
-    	return 	this.state; 
-    }
-}
-\end{lstlisting}
-
-The client code can directly use this \textit{enum} class method as below ``ToggleFlags.FEATURE1.isEnabled()'' which looks much cleaner in code when compared to accessing the values through constant variables.
-
-\subsection{Compile-Time Macros}
- used to interface with R language from the eclipse plugin.
+The BLR is calibration is done using the statistical tools like R or SPSS and JRI (Java R Inteface) is used to interface with R language from the eclipse plugin.
 The plugin operates in two different modes (local and remote).
@@
 \label{discussion}
-TODO
+we have listed the code smells that is incurred by the usage of feature toggles on a project.
+We have given names that define the characteristics of the smell and provided potential causes and consequences for each smell.
+The following toggle smells are covered
+\begin{enumerate}
+\item Dead toggles
+\item Nested toggles
+\item Spaghetti (Combinatorial) toggles
+\item Mix of compile-time and runtime toggles
+\item Stable toggles
+\item Spread toggles
+\end{enumerate}
+
+\subsection{TOGGLE_DEAD (Dead toggles)}
+\label{TOGGLE_DEAD}
 

### 2015-12-07 paper/paper.tex
writing code smells including tables

@@
 All XQuery instructions that depend on that path are dead code and maybe they should remove.
-For Static Code Refactoring they build an AST that consists in extracting all the path expressions from the program and checking their satisfiability individually.
+For Static Code Refactoring they build an AST parser that consists in extracting all the path expressions from the program and checking their satisfiability individually.
 Then, in a second step, these paths are combined with the schema, and checked again for satisfiability.
@@
 \subsection{Compile-Time Macros}
+TODO: Faruk
 
@@
 \label{discussion}
-we have listed the code smells that is incurred by the usage of feature toggles on a project.
+
+We have listed the code smells that is incurred by the usage of feature toggles on a project.
 We have given names that define the characteristics of the smell and provided potential causes and consequences for each smell.
-The following toggle smells are covered
+
+\subsection{TOGGLE\_DEAD (Dead toggles)}
+
+\begin{table}[ht]
+\caption{Dead Toggle Smell}
+\centering
+\begin{tabular}{|p{1.5cm}|p{7cm}|}
+ \hline\hline
+ Name & TOGGLE\_DEAD \\ \hline
+ Description & This smell is present if the toggle repository does not possess the information about the toggle flag, but the source code is still found to use the flags to encapsulate code blocks.
+\\ \hline
+ Example & 
+ \begin{lstlisting}
+if(switches::toggle1){
+    Do something
+}else{
+    Do something else
+}
+ \end{lstlisting}
+  \\ \hline
+
+ Possible reasons for their presence & The possible reasons why this smell is seen in the source code are:
  \begin{enumerate}
-\item Dead toggles
-\item Nested toggles
-\item Spaghetti (Combinatorial) toggles
-\item Mix of compile-time and runtime toggles
-\item Stable toggles
-\item Spread toggles
+ \item{The feature for which the toggle was added earlier became obsolete and the developers forgot to remove the toggle flag associated with the feature from the source code.}
+ \item{Developer has removed the toggle flag from the toggle repository unknowingly and hence causing this smell to appear.}
+ \item{There are no adequate test cases (functional/unit) to cover the code encapsulated under the toggle flag.
+If unit test cases were present to cover all the toggles in the toggle repository, this smell could be potentially identified by a test failure.}
+ \end{enumerate}
+ \\ \hline
+
+ Consequences & The presence of this smell has the following consequences in the project
+ \begin{enumerate}
+ \item{The presence of dead code.}
+ \item{If the feature is found not to be obsolete, then this smell could identify the corruption done to the toggle repository by an erroneous commit.}
+ \end{enumerate}
+ \\ \hline
+
+Possible Detection Algorithm & This smell can be detected using the following approach:
+ \begin{enumerate}
+ \item{The source code will be scanned for the expressions used for detecting the state of the toggle.
+This could involve scanning for an invocation of a particular API or static utility method to get the current value of the toggle.
+An expression in this context is appropriate language syntax involved in retrieving the state of the toggle from the toggle repository.}
+ \item{Typically the parameter used in this expression is the value of the toggle flag name.}
+ \item{The detector will check the toggle repository for the presence of this flag.}
+ \item{If the flag is absent in the toggle repository then this smell is detected.}
  \end{enumerate}
 
-\subsection{TOGGLE_DEAD (Dead toggles)}
-\label{TOGGLE_DEAD}
+ \\ \hline
+\end{tabular}
+\label{table:chrome-dir-data}
+\end{table}
 
@@
 
-Abstract syntax tree of the eclipse CDT API is utilized for each smell detection algorithm.
+Abstract syntax tree~\cite{AbstractSystaxTree} of the eclipse CDT API is utilized for each smell detection algorithm.
 The visitor designed pattern is applied on each of the source file to detect potential toggle smells.

### 2015-12-08 paper/paper.tex
Change the TSD to full abbreviation

@@
 Mix of Compile-Time and Runtime Toggles, Legacy toggles and Spread Toggles. 
-We created a tool ``TSD'' as an Eclipse plug-in using Eclipse C++ Development Tooling (CDT) to identify these toggle 
+We created a tool ``Toggle Smell Detector (TSD)'' as an Eclipse plug-in using Eclipse C++ Development Tooling (CDT) to identify these toggle 
 smells in major modules of Google Chrome source code. We found TODO 

### 2015-12-08 paper/paper.tex
Change some keyword and correct spelling

@@
 caused by improper use of feature toggles in Google Chrome that we call 
-as toggle smell. Using feature toggles to hide/unhide features is an old 
-concept but recently being practised in many software companies. Improper 
+as toggle smell. Using feature toggles to hide/show features is an old 
+concept but recently being practice in many software companies. Improper 
 use of toggles might cause code smell including duplicate code, dead code, 
@@
 in six different patterns Dead Toggles, Nested Toggles, Combinatorial (spaghetti) Toggles, 
-Mix of Compile-Time and Runtime Toggles, Legacy toggles and Spread Toggles. 
+Mix of Compile-Time and Runtime Toggles, Legacy/Stable toggles and Spread Toggles. 
 We created a tool ``Toggle Smell Detector (TSD)'' as an Eclipse plug-in using Eclipse C++ Development Tooling (CDT) to identify these toggle 

### 2015-12-08 paper/paper.tex
table of spread

--- 2015-12-07 paper/paper.tex
@@
 
+\subsection{TOGGLE\_SPAGHETTI (Combinatorial toggles)}
+
+\begin{table}[ht]
+\caption{Combinatorial Toggle Smell}
+\centering
+\begin{tabular}{|p{1.3cm}|p{7cm}|}
+ \hline\hline
+ Description & This smell is observed when the execution of code is controlled by combination of states of several toggles.  \\ \hline 
+ Example &  
+ \begin{lstlisting} 
+ 	//Location: /chrome/browser/about_flags.cc (taken from Google chrome)
+void FlagsState::
+ConvertFlagsToSwitches(FlagsStorage* flags_storage, 
+base::CommandLine* command_line, SentinelsMode sentinels) {
+if (command_line->
+HasSwitch(switches::kNoExperiments))
+return;
+
+std::set<std::string> enabled_experiments;
+//FlagsForCurrentPlatform = FFCP
+GetSanitizedEnabledFFCP
+(flags_storage, &enabled_experiments);
+
+NameToSwitchAndValueMap name_to_switch_map;
+for (size_t i = 0; i < num_experiments; ++i) {
+const Experiment& e = experiments[i];
+if (e.type == Experiment::SINGLE_VALUE) {
+	SetFlagToSwitchMapping(
+	e.internal_name, e.command_line_switch,
+	e.command_line_value, &name_to_switch_map
+	);
+} else if (e.type == Experiment::MULTI_VALUE) {
+		for (int j = 0; j < e.num_choices; ++j) {
+		SetFlagToSwitchMapping(
+		e.NameForChoice(j),
+		e.choices[j].command_line_switch,
+		e.choices[j].command_line_value,
+		&name_to_switch_map
+		);
+	}
+	} else {
+		DCHECK_EQ(e.type,
+		Experiment::ENABLE_DISABLE_VALUE);
+		SetFlagToSwitchMapping(
+		e.NameForChoice(0), std::string(), std::string(),
+		&name_to_switch_map
+		);
+
+		SetFlagToSwitchMapping(
+		e.NameForChoice(1), e.command_line_switch,
+		e.command_line_value, &name_to_switch_map
+		);
+		SetFlagToSwitchMapping(
+		e.NameForChoice(2), e.disable_command_line_switch,
+		e.disable_command_line_value, &name_to_switch_map
+		);
+		}
+	}
+}
+
+ \end{lstlisting}
+ \\ \hline
+
+ Possible reasons for their presence & 
+ \begin{enumerate}
+\item Mix of canary use cases or A/B testing in toggle block could result in this kind of spaghetti code.
+\item Inconsistency in API’s used to manage toggles and canary use cases.
+\item Presence of more than one API to manage feature flags. Transition from legacy feature toggles to more formal one.
+\end{enumerate}
+
+  \\ \hline
+ Name & TOGGLE\_DEAD \\ \hline
+ Name & TOGGLE\_DEAD \\ \hline
+ Name & TOGGLE\_DEAD \\ \hline
+
+\end{tabular}
+\label{table:chrome-dir-data}
+\end{table}
+
 \section{Our Approach}

### 2015-12-08 paper/paper.tex

@@
 in six different patterns Dead Toggles, Nested Toggles, Combinatorial (spaghetti) Toggles, 
-Mix of Compile-Time and Runtime Toggles, Legacy toggles and Spread Toggles. 
-We created a tool ``TSD'' as an Eclipse plug-in using Eclipse C++ Development Tooling (CDT) to identify these toggle 
+Mix of Compile-Time and Runtime Toggles, Legacy/Stable toggles and Spread Toggles. 
+We created a tool ``Toggle Smell Detector (TSD)'' as an Eclipse plug-in using Eclipse C++ Development Tooling (CDT) to identify these toggle 
 smells in major modules of Google Chrome source code. We found TODO 

### 2015-12-08 paper/paper.tex
resolving merge conflict

--- 2015-12-08 paper/paper.tex
@@
 as toggle smell. Using feature toggles to hide/show features is an old 
-concept but recently being practice in many software companies. Improper 
+concept but recently being practised in many software companies. Improper 
 use of toggles might cause code smell including duplicate code, dead code, 
@@
 in six different patterns Dead Toggles, Nested Toggles, Combinatorial (spaghetti) Toggles, 
-Mix of Compile-Time and Runtime Toggles, Legacy/Stable toggles and Spread Toggles. 
+Mix of Compile-Time and Runtime Toggles, Legacy toggles and Spread Toggles. 
 We created a tool ``Toggle Smell Detector (TSD)'' as an Eclipse plug-in using Eclipse C++ Development Tooling (CDT) to identify these toggle 
@@
  \hline\hline
- Name & TOGGLE\_DEAD \\ \hline
  Description & This smell is present if the toggle repository does not possess the information about the toggle flag, but the source code is still found to use the flags to encapsulate code blocks.
@@
  \\ \hline
+\end{tabular}
+\label{table:chrome-dir-data}
+\end{table}
+
+\begin{table}[ht]
+\caption{Dead Toggle Smell}
+\centering
+\begin{tabular}{|p{1.5cm}|p{7cm}|}
+\hline\hline
+ Description & This smell is observed when one toggle flag is dependent on the state of one or more other toggle flags. \\ \hline
+
+ Example & There are different patterns of this code smell similar to ``Message Chains''
+ \begin{enumerate}
+ \item{A variable might be used to store the state of the dependent toggles and will be used as a short circuit while checking the state of the actual feature flag.
+ \begin{lstlisting} 
+ boolean showF1Menu = ToggleService.isOn(“SHOW_F1_MENU”);
+
+ if(showF1Menu && ToggleService.isOn(“SHOW_F1_F11_MENU”) {
+ ….
+
+ }
+ \end{lstlisting}
+ }
+
+ \item{The code for the current feature will be under the encapsulation of a dependent feature toggle.
+ \begin{lstlisting}
+ if(ToggleService.isOn("F1")){
+   ...
+   if(ToggleService.isOn(“F11”)){
+   }
+   ...
+ }
+ \end{lstlisting}
+ } 
+ \end{enumerate}
+
+ \\ \hline
+
+ Possible reasons for their presence & This smell is found for one of the following possible reasons:
+ \begin{enumerate}
+ \item{Feature related to the nested toggles are related to each other. Existence of one feature depends on another feature. Features exhibit a composition relationship.
+  \begin{enumerate}
+  \item{For example if the main menu item is not enabled or made visible, then there is the submenus will not be visible or enabled.
+So in this scenario the code turn on the submenus will be encapsulated under the toggle flag check of the main menu item.}
+  \end{enumerate}
+ }
+ \item{Sometimes a master toggle switch is used to turn on/off many closely related features.
+  \begin{enumerate}
+  \item{In some software segment like e-commerce/online gambling/gaming, a set of features will be targeted for audience of a particular region, in these scenarios a master toggle is used to control the dark launch all/some of the features.}
+  \end{enumerate}
+ }
+ \end{enumerate}
+
+ \\ \hline
+ Consequences & Too many levels of nesting will add to the cost of testing the changes so as to cover all code paths with state on/off.
+ \\ \hline
+
+ Detection & This smell could be detected using the following approach.\\
+ \begin{enumerate}
+ \item{In order to identify potential positive instances of this smell, the detector could use trained patterns using a mathematical model like BLR(Binary Logistic Regression).}
+ \item{Or simple level count could be used to identify the smell.
+Say for example if the number of nested toggles levels is greater than 2 then there is a possibility of the presence of this code smell.}
+ \item{Also the detector can be enhanced to identify that there is a common master toggle used for the most of the nested toggles and could be prevented in identifying false smells.}
+ \end{enumerate}
+
+ \\ \hline
+
 \end{tabular}

### 2015-12-08 paper/paper.tex
add the TOGGLE_STABLE and Mix Toggle

--- 2015-12-08 paper/paper.tex
@@
 
+\subsection{Mix of Compile time and run-time toggles)}
+
+\begin{table}[ht]
+\caption{TOGGLE\_MIX}
+\centering
+\begin{tabular}{|p{1.5cm}|p{7cm}|}
+ \hline\hline
+ Description & This smell is observed when the source code uses multiple techniques to manage toggles.
+One such usage is to combine compile time (\#define, \#ifndef) along with run time toggles.
+\\ \hline
+
+ Example & 
+ \begin{lstlisting}
+ //Location: /chrome/app/chrome_main_delegate.cc (Taken from Google chrome)
+#if defined(OS_MACOSX)
+// Mac needs them too for scrollbar related images and for sandbox
+// profiles.
+#if !defined(DISABLE_NACL)
+process_type == switches::kNaClLoaderProcess ||
+#endif
+process_type == switches::kPpapiPluginProcess ||
+process_type == switches::kPpapiBrokerProcess ||
+process_type == switches::kGpuProcess ||
+#endif
+process_type == switches::kRendererProcess ||
+process_type == switches::kUtilityProcess;
+}
+ \end{lstlisting}
+
+ \\ \hline
+
+Possible reasons for their presence & 
+\begin{enumerate}
+	\item This is in general observed when the code is based on compiled languages where conditional compilation prevents unnecessary changes from being included into the target binary (to reduce size).
+But unfortunately within those statements the feature toggle statements are also included.
+\end{enumerate}	 
+ \\ \hline
+ Consequences & 
+ Presence of this smell indicates the following possible consequences
+ \begin{enumerate}
+	\item Cost of testing will increase so as to cover all the code paths with different binary versions.
+\end{enumerate}
+ \\ \hline
+
+ Detection & TBD \\ \hline
+\end{tabular}
+\label{table:chrome-dir-data}
+\end{table}
+
+\subsection{TOGGLE\_STABLE (Stable Toggles)}
+
+\begin{table}[ht]
+\caption{TOGGLE\_STABLE}
+\centering
+\begin{tabular}{|p{1.3cm}|p{7cm}|}
+ \hline\hline
+ Description & This smell is observed when the feature has received enough feedback from the production environment and has been observed stable through several releases and became permanent in the product.
+However the code for the features are still running with the toggle check.
+\\ \hline
+
+Example & Not Applicable \\ \hline
+Possible reasons for their presence & There is a lack of discipline in managing the lifecycle of the toggle in the organisation or in the project. \\ \hline
+Example & Not Applicable \\ \hline
+Consequences & Presence of this smell indicates the following possible consequences in the
+\begin{enumerate}
+	\item This is rated as the one of the worst technical debt for any source code as it will become non-trivial to remove the toggled code block for all features which are stable in the production late in the cycle.
+\item The changes done to remove the toggled code block will cost regression and testing cycle.
+\item By the time, a plan is derived there might be several other toggles that will be part of the source which might complicate the elimination of this stable toggle. 
+\end{enumerate}
+\\ \hline
+
+\end{tabular}
+\label{table:chrome-dir-data}
+\end{table}
+
 \section{Our Approach}

### 2015-12-08 paper/paper.tex
fixing tables

@@
 \usepackage{enumitem}
+\usepackage{float}
 
@@
 
-\subsection{TOGGLE\_DEAD (Dead toggles)}
+\subsection{TOGGLE\_DEAD (Dead Toggles)}
 
@@
 \end{tabular}
-\label{table:chrome-dir-data}
+\label{table:dead-toggle}
 \end{table}
 
-\begin{table}[ht]
-\caption{Dead Toggle Smell}
+\subsection{TOGGLE\_NEST (Nested Toggles)}
+\begin{table}[!htbp]
+\caption{Nested Toggle Smell}
 \centering
-\begin{tabular}{|p{1.5cm}|p{7cm}|}
+\begin{tabular}{|p{1.5cm}|p{6.6cm}|}
 \hline\hline
@@
  \begin{lstlisting} 
- boolean showF1Menu = ToggleService.isOn(“SHOW_F1_MENU”);
+ boolean s = functionX();
 
- if(showF1Menu && ToggleService.isOn(“SHOW_F1_F11_MENU”) {
- ….
-
+ if(s && functionX()) {
+    ...
  }
@@
  \\ \hline
+
  Consequences & Too many levels of nesting will add to the cost of testing the changes so as to cover all code paths with state on/off.
@@
 
- Detection & This smell could be detected using the following approach.\\
+ Detection & This smell could be detected using the following approach.
   \begin{enumerate}
@@
 \end{tabular}
-\label{table:chrome-dir-data}
+\label{table:toggle-nest}
 \end{table}
+\newpage
 
-\subsection{Mix of Compile time and run-time toggles)}
+\subsection{TOGGLE\_MIX (Mix of compile-time and run-time toggles)}
 
-\begin{table}[ht]
+\begin{table}[h]
 \caption{TOGGLE\_MIX}
 \centering
-\begin{tabular}{|p{1.5cm}|p{7cm}|}
+\begin{tabular}{|p{1.5cm}|p{6.6cm}|}
  \hline\hline
@@
  \begin{lstlisting}
- //Location: /chrome/app/chrome_main_delegate.cc (Taken from Google chrome)
-#if defined(OS_MACOSX)
-// Mac needs them too for scrollbar related images and for sandbox
-// profiles.
-#if !defined(DISABLE_NACL)
+ #if
  process_type == switches::kNaClLoaderProcess ||
@@
  process_type == switches::kPpapiPluginProcess ||
-process_type == switches::kPpapiBrokerProcess ||
-process_type == switches::kGpuProcess ||
+ process_type == switches::kPpapiBrokerProcess
  #endif
-process_type == switches::kRendererProcess ||
-process_type == switches::kUtilityProcess;
-}
  \end{lstlisting}

### 2015-12-08 paper/paper.tex
Add the result section

--- 2015-12-08 paper/paper.tex
@@
 \label{threats}
-TODO
-\subsection{Qualitative}
-TODO
-\subsection{Quantitative}
-TODO
+
+To get quantitative and qualitative results we did the following tasks:
+
+\begin{itemize}
+\item Classified the list of modules which has cpp source units. We derived this list by using native OS commands like GREP, FIND on Linux system.
+\item The list of modules within chrome project and their total of cpp files within each module is presented in the table <table num>
+\item From that list we picked up 7 modules which has high number of C++ source files (Greater than 500).
+\item We ran our smell detection program on each of the modules to find potential toggle smells.
+\item The results are shown in the table
+\item From the table below we can observe that NESTED\_TOGGLE smell is quite high in number when compared to other smell types.
+In the module by name “chrome” which has the highest number of C++ compilation units, the NESTED toggle smells have been found in huge number (109) when compared to all other modules.
+\end{itemize}
+
+\subsection{Verification of results}
+\label{Result Varification}
+Except for the module “chrome”, we manually verified and confirmed that smells reported by algorithm are indeed presence in the code and not a false positive.
+Also for the modules of lesser size like ppapi, where no smells were found by the detector, we manually checked the source code for potential code smells by using the eclipse search by file and search by references feature.
+We invoked a search by references for the API invoking the toggle method name.
+Though there were instances of method invocations, there were not any potential code smells observed through manual inspection.
+
+\subsection{No Dead or Stable Toggle Smell}
+For our study we have taken the latest version of chromium project source code using the ``\textbf{depot\_tools}''.
+However for the current version we didn’t had historical data of the dead toggles.
+So in order to validate the dead toggle detection algorithm, we manually induced the smells in the code and verified that our algorithm is working as designed.
+\\
+
+So to confirm the behavior, we also took the earlier version of the code from the repository and ran the dead toggle smell detection algorithm and we found the following results.
+This prove that algorithm was indeed able to detect smells in the actual code.
 

### 2015-12-08 paper/paper.tex
add the result table

--- 2015-12-08 paper/paper.tex
@@
 \label{threats}
-TODO
+\begin{table*}[ht]
+\caption{Number of Smells}
+\centering
+\begin{tabular}{|p{2.1cm}|p{2.1cm}|p{2.1cm}|p{2.1cm}|p{2.1cm}|p{2.1cm}|p{2.1cm}|}
+ \hline\hline
+Module Name & Num Files & Nested Toggle \#Smells & Spread Toggle \#Smells & Combinatorial Toggle \#Smells &  Dead Toggle \#Smells & Average time to scan/Smell \\ \hline
+
+Base & 749 & 1 & 5 & 4  & 0 & 1556013 ms \\ \hline
+UI & 1501 & 2 & 1 & 0  & 0 & 888080 ms \\ \hline
+Net & 1534 & 16 & 0 & 9  & 0 & 927508 ms \\ \hline
+Media & 746 & 16 & 0 & 9  & 0 & 370563 ms \\ \hline
+ppapi & 563 & 0 & 0 & 0  & 0 & 944816 ms \\ \hline
+ash & 502 & 1 & 1 & 0  & 0 & 390563 ms \\ \hline
+chrome & 6105 & 109 & 31 & 24  & 0 & 2468547 ms \\ \hline
+
+\end{tabular}
+\label{table:chrome-result-data}
+\end{table*}
+
 \subsection{Qualitative}

### 2015-12-08 paper/paper.tex
Add rest of the result section

--- 2015-12-08 paper/paper.tex
@@
 
+\subsection{Average Running time}
+The program takes on an average 6 minutes to scan a project containing about 700 to 1000 source files.
+The scan time is proportional to the number of source files as well as the number of expressions and statements in each file.
+
 \section{Limitations}
@@
 \label{conclusion}
-TODO
+The implementation of the toggle smell detector is practically usable for project using feature toggles.
+The time taken by the detector is proportional to the size of the project and the smells detected indeed indicate the common problems with the object oriented software like high coupling, low cohesion.
+Our approach will save lot of time for developers and designers to identify the toggle code smells in source code project, compared to the other approaches like searching through native OS commands or using IDE provided search by reference techniques, which may not accurately indicate a particular smell like spread toggle as it requires examining each toggle flag at various locations.
 

### 2015-12-08 paper/paper.tex

--- 2015-12-08 paper/paper.tex
@@
 
+\begin{table*}[ht]
+\caption{Number of Smells}
+\centering
+\begin{tabular}{|p{2.1cm}|p{2.1cm}|p{2.1cm}|p{2.1cm}|p{2.1cm}|p{2.1cm}|p{2.1cm}|}
+ \hline\hline
+Module Name & Num Files & Nested Toggle \#Smells & Spread Toggle \#Smells & Combinatorial Toggle \#Smells &  Dead Toggle \#Smells & Average time to scan/Smell \\ \hline
+
+Base & 749 & 1 & 5 & 4  & 0 & 1556013 ms \\ \hline
+UI & 1501 & 2 & 1 & 0  & 0 & 888080 ms \\ \hline
+Net & 1534 & 16 & 0 & 9  & 0 & 927508 ms \\ \hline
+Media & 746 & 16 & 0 & 9  & 0 & 370563 ms \\ \hline
+ppapi & 563 & 0 & 0 & 0  & 0 & 944816 ms \\ \hline
+ash & 502 & 1 & 1 & 0  & 0 & 390563 ms \\ \hline
+chrome & 6105 & 109 & 31 & 24  & 0 & 2468547 ms \\ \hline
+
+\end{tabular}
+\label{table:chrome-result-data}
+\end{table*}
+
 To get quantitative and qualitative results we did the following tasks:
@@
 
-\subsection{Verification of results}
+\subsection{Verification of Results}
 \label{Result Varification}

### 2015-12-08 paper/paper.tex
Adding the Future Improvements section

--- 2015-12-08 paper/paper.tex
@@
 
-and the vice versa variant.
+and the vice verse variant.
 It will not detect if there is a complex conditional expression if used within the conditional statement.
@@
 
+\section{Future Improvements}
+\label{Future Improvements}
+We feel the following improvements are possible in the tool based on the direction it is being extended.
+
+\begin{enumerate}
+
+\item{Overall time improvement
+\begin{itemize}
+\item At present each algorithm is ran sequentially, which could be improved by using multiple threads to run each algorithm in a parallel thread which can improve the overall time taken for detecting all smells in a source code module.
+\end{itemize}
+}
+
+\item{User interface
+\begin{itemize}
+\item At present there is no user interface support and results are directed to the console view or could be directed to an output file from the eclipse run configuration.
+\item But if user interface is desired, then a menu option could be provided to run each detection algorithm separately.
+This way the tool will facilitate the developers intend to fix only a particular type of toggle code smell, which also saves time.
+\end{itemize}
+}
+
+\item{Avoiding ‘N’ passes
+\begin{itemize}
+\item At present for each smell detection type, the algorithm scans the same set of files again and again.
+This would lead to scaling problem when ran on a large module.
+We have already observed with the results indicating 41 minutes to scan the “chrome” module for each smell detection.
+This is significant problem with the current algorithm.
+\item Instead a common data structure could be built by a single pass of the entire source code which could be leveraged by each smell detection algorithm. This has the following advantages
+\end{itemize}
+}
+
+\item{User interface
+\begin{itemize}
+\item 
+\item
+\end{itemize}
+}
+
+\end{enumerate}
+
 \section{Conclusion}

### 2015-12-08 paper/paper.tex
merging
adding float
Add Threats to validity

--- 2015-12-08 paper/paper.tex
@@
 This is significant problem with the current algorithm.
-\item Instead a common data structure could be built by a single pass of the entire source code which could be leveraged by each smell detection algorithm. This has the following advantages
+\item {
+Instead a common data structure could be built by a single pass of the entire source code which could be leveraged by each smell detection algorithm. This has the following advantages
+  \begin{enumerate}
+  \item Overall running time for all the algorithm improves significantly.
+  \item Each smell detector does not need to scan the entire source file and build the abstract syntax trees.
+The common data structure could be leveraged to go to particular location within the source and perform a coarse grained search.
+   \item Some files where there are no toggle method invocations will be ignored by each of the smell detection algorithms.
+For example, currently if there are ‘N’ files which does not have any toggle method invocation, then each file is parsed and AST is generated and then it is checked further.
+This overhead time will be saved.
+  \end{enumerate}
+}
 \end{itemize}
@@
 
-\item{User interface
+\item{Automatic detection of dead/stable toggles
 \begin{itemize}
-\item 
-\item
+\item Our approach currently expects list of dead/stable toggles to be provided as an input by the user.
+But this could be avoided if alternate MSR techniques are implemented to detect the code chunks which involves changing the state of the toggle flags in test and live environment and derive the list of stable/dead toggles in an automated way.
+However we don’t have any approach in thought as of now.
 \end{itemize}
+}
+\end{enumerate}
+
+\section{Threats to validity}
+\label{Threats to validity}
+
+Though we have done extensive study on google chromium project and came up with classification of code smells, we haven’t done exploratory study on other projects to confirm the presence of toggle smells we defined in this research.
+There are several reasons for this
+
+\begin{enumerate}
+\item{Not many open source projects are using feature toggles.
+\begin{enumerate}
+\item In our search we found only one more project in the github location named “go.cd” which has feature toggle implementation. But the project was using JRuby and Java as the primary languages.
+\end{enumerate}
+}
+\item {No evolution history of toggle usage
+\begin{enumerate}
+\item Google chrome project has been using feature toggles for more than 5 years and has an evolution history to mine the source code repository.
+We are yet to find another project which has the evolution and data to mine.
+\end{enumerate}
 }

### 2015-12-08 paper/paper.tex
fixing tables

--- 2015-12-08 paper/paper.tex
@@
 In our research objective we have to classify the code smells related to the usage of features toggles.
-One such code smell is to identify the distribution of the same toggles flag among various sources files, we have named this as “TOGGLE SPREAD”.
+One such code smell is to identify the distribution of the same toggles flag among various sources files, we have named this as ``TOGGLE SPREAD''.
 This indicates the loose cohesion of a feature.
@@
 
-Pierre Genevès and Nabil Layaïda~\cite{geneves2010eliminating} studied how to detect and remove dead code from Xquery programs.
-They propose a technique for performing static basic dead-code analysis and eliminate the dead code from an XQuery program.
-XQuery is a query and functional programming language basically takes one (or possibly several) XML document as input, performs some computation based on its tree view, and finally outputs a result in the form of another XML document.
-The core of the XQuery language is composed of XPath expressions that make it possible to navigate in the document tree and extract nodes that satisfy some conditions.
-They use two methodology \textbf{Path-Error Detection} and \textbf{Static Code Refactoring and Highlighting}.
 In the path-error detection they gave a scema as input to an XQuery program and For each XPath expression occurring in XQuery program, they just check that it is meaningful or not with respect to the constraints described in scema.
@@
 
-\begin{table}[ht]
+\begin{table}[!h]
 \caption{Dead Toggle Smell}
 \centering
-\begin{tabular}{|p{1.5cm}|p{7cm}|}
+\begin{tabular}{|p{1.5cm}|p{6.6cm}|}
  \hline\hline
@@
 \end{tabular}
-\label{table:chrome-dir-data}
+\label{table:toggle-dead}
 \end{table}
 
-\begin{table}[ht]
-\caption{Dead Toggle Smell}
+\subsection{TOGGLE\_NEST (Nested Toggles)}
+\begin{table}[!h]
+\caption{Nested Toggle Smell}
 \centering
-\begin{tabular}{|p{1.5cm}|p{7cm}|}
+\begin{tabular}{|p{1.5cm}|p{6.6cm}|}
 \hline\hline
@@
  \begin{lstlisting} 
- boolean showF1Menu = ToggleService.isOn(“SHOW_F1_MENU”);
+ boolean s = functionX();
 
- if(showF1Menu && ToggleService.isOn(“SHOW_F1_F11_MENU”) {
- ….
-
+ if(s && functionX()){
+ ...
  }
@@
 
- Detection & This smell could be detected using the following approach.\\
- \begin{enumerate}
- \item{In order to identify potential positive instances of this smell, the detector could use trained patterns using a mathematical model like BLR(Binary Logistic Regression).}
- \item{Or simple level count could be used to identify the smell.
-Say for example if the number of nested toggles levels is greater than 2 then there is a possibility of the presence of this code smell.}
- \item{Also the detector can be enhanced to identify that there is a common master toggle used for the most of the nested toggles and could be prevented in identifying false smells.}
- \end{enumerate}
-
- \\ \hline
-
 \end{tabular}
-\label{table:chrome-dir-data}
+\label{table:nested-toggle}
 \end{table}
 
-\subsection{Mix of Compile time and run-time toggles)}
+\subsection{TOGGLE\_MIX (Mix of compile-time and run-time toggles)}
 
-\begin{table}[ht]
+\begin{table}[!h]
 \caption{TOGGLE\_MIX}
 \centering
-\begin{tabular}{|p{1.5cm}|p{7cm}|}
+\begin{tabular}{|p{1.5cm}|p{6.6cm}|}
  \hline\hline
@@
  \begin{lstlisting}
- //Location: /chrome/app/chrome_main_delegate.cc (Taken from Google chrome)
-#if defined(OS_MACOSX)
-// Mac needs them too for scrollbar related images and for sandbox
-// profiles.
-#if !defined(DISABLE_NACL)
+#if
 process_type == switches::kNaClLoaderProcess ||
@@
 process_type == switches::kPpapiPluginProcess ||
-process_type == switches::kPpapiBrokerProcess ||
-process_type == switches::kGpuProcess ||
+process_type == switches::kGpuProcess
 #endif
-process_type == switches::kRendererProcess ||
-process_type == switches::kUtilityProcess;
 }
@@
 
- Detection & TBD \\ \hline
 \end{tabular}
-\label{table:chrome-dir-data}
+\label{table:mix-toggle}
 \end{table}
@@
 
-\begin{table}[ht]
+\begin{table}[!h]
 \caption{TOGGLE\_STABLE}
 \centering
-\begin{tabular}{|p{1.3cm}|p{7cm}|}
+\begin{tabular}{|p{1.5cm}|p{6.6cm}|}
  \hline\hline

### 2015-12-08 paper/paper.tex

@@
 
-\begin{table*}[ht]
-\caption{Number of Smells}
-\centering
-\begin{tabular}{|p{2.1cm}|p{2.1cm}|p{2.1cm}|p{2.1cm}|p{2.1cm}|p{2.1cm}|p{2.1cm}|}
- \hline\hline
-Module Name & Num Files & Nested Toggle \#Smells & Spread Toggle \#Smells & Combinatorial Toggle \#Smells &  Dead Toggle \#Smells & Average time to scan/Smell \\ \hline
-
-Base & 749 & 1 & 5 & 4  & 0 & 1556013 ms \\ \hline
-UI & 1501 & 2 & 1 & 0  & 0 & 888080 ms \\ \hline
-Net & 1534 & 16 & 0 & 9  & 0 & 927508 ms \\ \hline
-Media & 746 & 16 & 0 & 9  & 0 & 370563 ms \\ \hline
-ppapi & 563 & 0 & 0 & 0  & 0 & 944816 ms \\ \hline
-ash & 502 & 1 & 1 & 0  & 0 & 390563 ms \\ \hline
-chrome & 6105 & 109 & 31 & 24  & 0 & 2468547 ms \\ \hline
-
-\end{tabular}
-\label{table:chrome-result-data}
-\end{table*}
-
 To get quantitative and qualitative results we did the following tasks:
@@
 
-\subsection{Verification of Results}
+\subsection{Verification of results}
 \label{Result Varification}

### 2015-12-08 paper/paper.tex
Fix something in the result
Add the TODO in the introduction paragraph

@@
 \usepackage{enumitem}
-\usepackage{float}
 
@@
 We created a tool ``Toggle Smell Detector (TSD)'' as an Eclipse plug-in using Eclipse C++ Development Tooling (CDT) to identify these toggle 
-smells in major modules of Google Chrome source code. We found TODO 
-nested toggles smells, TODO spaghetti toggles and TODO spread toggles in ``chrome'' and ``base'' modules of Google Chrome.\\
+smells in major modules of Google Chrome source code. We found 130 
+nested toggles smells, 37 spaghetti toggles and 37 spread toggles in  the following modules namely base, ui, net, media, ppapi, ash, chrome.
+In total we found 206 different toggle related code smells in 7 different modules from google chromium project.\\
 \end{abstract}
@@
 In order to explore the feature toggle related smell we have searched for open source projects and found some projects with feature toggle implemented in those project.
-But we have choose Google chromium as our main code base because it has more then 5 years active development life cycle with feature toggle in it and it has rapid released.
-So there might be any issue with feature toggle which might not notice properly.
+But we have choose Google chromium as our main code base because it has more then 5 years active development life cycle with feature toggle in it and it has rapid releases.
 We have used Eclipse Plugin Development Environment(PDE) which is a Java based framework, it provides support for building source code analysis applications.
@@
 \centering
-\begin{tabular}{|p{1.5cm}|p{6.6cm}|}
+\begin{tabular}{|p{1.5cm}|p{7cm}|}
  \hline\hline
@@
 
-\begin{table}[!h]
+\begin{table}[ht]
 \caption{TOGGLE\_STABLE}
@@
 So in order to validate the dead toggle detection algorithm, we manually induced the smells in the code and verified that our algorithm is working as designed.
-\\
-
-So to confirm the behavior, we also took the earlier version of the code from the repository and ran the dead toggle smell detection algorithm and we found the following results.
-This prove that algorithm was indeed able to detect smells in the actual code.
 

### 2015-12-08 paper/paper.tex
finised Macro

--- 2015-12-08 paper/paper.tex
@@
 \section{Case Study}
-\label{results}
+\label{case-study}
 We classified toggle smells in different classes based on their usage in 
@@
 available in Google Chrome.
-
-\subsection{Compile Time toggles}
+\subsection{Toggle Pattern}
+First we will list out the possible ways of using feature toggles in any project, some of which might depend on the availability of feature toggle framework in programming languages.
+\subsubsection{Compile Time Toggles}
 The first set of usage patterns we descriptively belongs to the compile 
@@
 
-\subsection{Constants and Variables}
+\subsubsection{Constants and Variables}
 In this pattern the value of the toggle state of a feature is managed through a constant variable declared in the program.
@@
 
-\subsection{Enumerations}
+\subsubsection{Enumerations}
 In Java there is a support to manage set of states through “enum” interface which is much richer when compared to languages like C, C++ (C++11 has similar support).
@@
 
-\subsection{Compile-Time Macros}
-TODO: Faruk
+\subsubsection{Compile-Time Macros}
+This kind of usage is predominant in languages which support macros (C, C++) and used for conditional compilation.
+This violates the fundamental principle of the feature toggles.
+Even though feature toggle experts does not recommend this approach, some still prefer to use.
+\begin{lstlisting}
+#ifdef FEATURE1
+….
+#endif
+\end{lstlisting}
+
+\subsection{Run time toggles}
+Run time toggles usage comes in two flavors, in one the state of the feature flags will be modified without restarting the program or service managing the feature, in another flavor the toggle value will be changed, but requires restart of the program or service.
+The deployment model depends on the infrastructure of the target environment.
+The advantage of the run time toggle when compared to the compile time toggles is that they don’t require touching the source code file and regenerate the binary.
+In languages similar to Javascript, where binary generation is not required because of the execution model, keeping the toggle repository separate from the source code (in the form of JSON) will prevent the minification process.
+\subsubsection{Live Update With Program Restart}
+In this usage, the toggle flags value will be changed and new toggle values will come into effect only when the program or service is restarted.
+Though this will have an impact on the availability of the service or program for the duration of the restart, the impact could be minimized by scheduling the toggle changes to the off-peak load hours.
+But if the program restart time is not significant and if there is a high availability setup in place, then this process will give good benefits.
+There are different ways to doing this:
+\begin{itemize}
+\item External files (.json, .properties, .csv) with one time loading
+\item Command Line Arguments
+\item Live update without program restart
+\item External files with auto reloading
+\item Private API or Interface to change toggle state
+\end{itemize}
 

### 2015-12-08 paper/paper.tex
Delete unnecessary table row

--- 2015-12-08 paper/paper.tex
@@
 
-Possible Detection Algorithm & This smell can be detected using the following approach:
- \begin{enumerate}
- \item{The source code will be scanned for the expressions used for detecting the state of the toggle.
-This could involve scanning for an invocation of a particular API or static utility method to get the current value of the toggle.
-An expression in this context is appropriate language syntax involved in retrieving the state of the toggle from the toggle repository.}
- \item{Typically the parameter used in this expression is the value of the toggle flag name.}
- \item{The detector will check the toggle repository for the presence of this flag.}
- \item{If the flag is absent in the toggle repository then this smell is detected.}
- \end{enumerate}
-
- \\ \hline
 \end{tabular}

### 2015-12-08 paper/paper.tex
merging

--- 2015-12-08 paper/paper.tex
@@
 Feature oriented Model Driven Development allows us develop software system to grow up in a feature oriented way that dictates the features to be distinguishable and understandable.
-To develop features in an isolated way while developing on a single trunk major software companies including Google~\cite{ChromeRepidRelease}, Facebook~\cite{Rossi2014Google} and Netflix use feature toggles to enable or disable a feature from the end-user access.
+To develop features in an isolated way while developing on a single trunk major software companies including Google~\cite{ChromeRepidRelease}, Facebook~\cite{Rossi2014Google} and Netflix~\cite{NetFlixCasandra} use feature toggles to enable or disable a feature from the end-user access.
 However, improper use of feature toggles is a bad practice~\cite{Fowler2010FeatureToggle}.
@@
 \subsection{Compile-Time Macros}
-TODO: Faruk
+This kind of usage is predominant in languages which support macros (C, C++) and used for conditional compilation.
+This violates the fundamental principle of the feature toggles.
+Even though feature toggle experts does not recommend this approach, some still prefer to use.
+\begin{lstlisting}
+#ifdef FEATURE1
+….
+#endif
+\end{lstlisting}
+
+\subsection{Run time toggles}
+Run time toggles usage comes in two flavors, in one the state of the feature flags will be modified without restarting the program or service managing the feature, in another flavor the toggle value will be changed, but requires restart of the program or service.
+The deployment model depends on the infrastructure of the target environment.
+The advantage of the run time toggle when compared to the compile time toggles is that they don’t require touching the source code file and regenerate the binary.
+In languages similar to Javascript, where binary generation is not required because of the execution model, keeping the toggle repository separate from the source code (in the form of JSON) will prevent the minification process.
+
+There are different ways to doing this:
+
+\subsubsection{Live Update With Program Restart}
+
+\begin{itemize}
+\item External files (.json, .properties, .csv) with one time loading
+\item Command Line Arguments
+\end{itemize}
+
+\subsubsection{Live update without program restart}
+\begin{itemize}
+\item External files with auto reloading
+\item Private API or Interface to change toggle state
+\end{itemize}
 
@@
 This is significant problem with the current algorithm.
-\item {
-Instead a common data structure could be built by a single pass of the entire source code which could be leveraged by each smell detection algorithm. This has the following advantages
-  \begin{enumerate}
-  \item Overall running time for all the algorithm improves significantly.
-  \item Each smell detector does not need to scan the entire source file and build the abstract syntax trees.
-The common data structure could be leveraged to go to particular location within the source and perform a coarse grained search.
-   \item Some files where there are no toggle method invocations will be ignored by each of the smell detection algorithms.
-For example, currently if there are ‘N’ files which does not have any toggle method invocation, then each file is parsed and AST is generated and then it is checked further.
-This overhead time will be saved.
-  \end{enumerate}
-}
+\item Instead a common data structure could be built by a single pass of the entire source code which could be leveraged by each smell detection algorithm. This has the following advantages
 \end{itemize}
@@
 
-\item{Automatic detection of dead/stable toggles
+\item{User interface
 \begin{itemize}
-\item Our approach currently expects list of dead/stable toggles to be provided as an input by the user.
-But this could be avoided if alternate MSR techniques are implemented to detect the code chunks which involves changing the state of the toggle flags in test and live environment and derive the list of stable/dead toggles in an automated way.
-However we don’t have any approach in thought as of now.
+\item 
+\item
 \end{itemize}
-}
-\end{enumerate}
-
-\section{Threats to validity}
-\label{Threats to validity}
-
-Though we have done extensive study on google chromium project and came up with classification of code smells, we haven’t done exploratory study on other projects to confirm the presence of toggle smells we defined in this research.
-There are several reasons for this
-
-\begin{enumerate}
-\item{Not many open source projects are using feature toggles.
-\begin{enumerate}
-\item In our search we found only one more project in the github location named “go.cd” which has feature toggle implementation. But the project was using JRuby and Java as the primary languages.
-\end{enumerate}
-}
-\item {No evolution history of toggle usage
-\begin{enumerate}
-\item Google chrome project has been using feature toggles for more than 5 years and has an evolution history to mine the source code repository.
-We are yet to find another project which has the evolution and data to mine.
-\end{enumerate}
 }

### 2015-12-08 paper/paper.tex
adding another table

--- 2015-12-08 paper/paper.tex
@@
 
+\subsection{TOGGLE\_SPAGHETTI (Combinatorial Toggles)}
+\begin{table}[!h]
+\caption{TOGGLE\_SPAGHETTI}
+\centering
+\begin{tabular}{|p{1.5cm}|p{6.6cm}|}
+ \hline\hline
+ Description & This smell is observed when the execution of code is controlled by combination of states of several toggles.  \\ \hline
+
+ Example & 
+ \begin{lstlisting}
+ if(command_line->HasSwitch(
+     s::kTestLauncherTotalShards) &&
+     command_line->HasSwitch(
+         s::kTestLauncherShardIndex)
+     ){
+ if(!StringToInt(
+      command_line
+      ->GetSwitchValueASCII(
+          s::kTestLauncherTotalShards),
+          &total_shards)){
+      LOG(ERROR) << "Invalid value for " <<    
+      s::kTestLauncherTotalShards;
+      return false;
+  }
+ \end{lstlisting}
+ \\ \hline
+
+ Possible reasons for their presence &
+
+ \begin{enumerate}
+ \item{Mix of canary use cases or A/B testing in toggle block could result in this kind of spaghetti code.}
+ \item{Inconsistency in API’s used to manage toggles and canary use cases.}
+ \item{Presence of more than one API to manage feature flags. Transition from legacy feature toggles to more formal one.}
+ \end{enumerate}
+ \\ \hline
+
+ Consequences & If this smell is observed it will have the following consequences in the project
+Cost of testing will increase so as to cover all the code paths.
+Changing existing code base will become non-trivial.
+Code complexity is higher, difficult to understand.
+ \\ \hline
+
+\end{tabular}
+\label{table:chrome-dir-data}
+\end{table}
+
 \section{Our Approach}
@@
 
+\begin{figure*}
+\includegraphics[height=6in,width=7in]{figure/uml.png}
+\caption{UML Class Diagram.}
+\label{fig:uml}
+\end{figure*}
+
 \section{Implementation Details And Algorithm}
@@
 \textbf{Toggle method signature or function name:} Without this information the toggle smell detector could not search for the pattern of the method used to check the toggle usage.
+Figure~\ref{fig:uml} represents the design of our
+approach in an UML diagram.
 
